# (PART) Part - Descriptive Statistics {-}


# Socio-demographics

```{r echo=FALSE, warning=FALSE, message=FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE, 
  message = FALSE, 
  warning = FALSE,
  comment = "#>"
)


library(tidyverse)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(RColorBrewer)

source("util/util.fn.R")

load("~/Documents/limbo/df_369612_20DEC2019.rdata")

pal2 <-  brewer.pal(2, "Set1")
pal3 <-  brewer.pal(3, "Set1")
pal4 <-  brewer.pal(4, "Set1")
pal5 <-  brewer.pal(5, "Set1")
pal6 <-  brewer.pal(6, "Set1")
pal7 <-  brewer.pal(7, "Set1")

hideNA = T

```


## Core demographics: age, gender, ...

###  `r if (!is.null(data$SDEM001)) get_label(data$SDEM001)`

```{r year_born, eval=!is.null(data$SDEM001)}

data %>% 
    mutate(age = SDEM001) %>% 
    ggplot(aes(x=SDEM001)) + 
    geom_bar()+ 
    labs(title="") +
    theme_light() +
    theme(axis.title.x = element_blank())

```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$SDEM004)) get_label(data$SDEM004)`
```{r gender, eval=!is.null(data$SDEM004), fig.align='center'}

data %>% 
    filter(!is.na(SDEM004) & hideNA) %>% 
    ggplot(aes(x=SDEM004, fill=SDEM004)) + 
    geom_bar(width=.5) +
    scale_fill_manual(values=pal2) +
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.x = element_blank())
```

<p>&nbsp;</p>

```{r gender_tab, eval=!is.null(data$SDEM004)}

print_frqtable(data$SDEM004)
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$SDEM007)) get_label(data$SDEM007)`
```{r sex_orientation, eval=!is.null(data$SDEM007)}

data %>% 
    filter(!is.na(SDEM007) & hideNA) %>% 
    ggplot(aes(x=SDEM007, fill=SDEM007)) + 
    geom_bar(width=.5) +
    scale_fill_manual(values=pal4) +
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.x = element_blank())
```



```{r sex_orientation_tab, eval=!is.null(data$SDEM007)}

print_frqtable(data$SDEM007) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$SDEM009)) get_label(data$SDEM009)`
```{r disability, eval=!is.null(data$SDEM009)}

data %>% 
    filter(!is.na(SDEM009) & hideNA) %>% 
    ggplot(aes(x=SDEM009, fill=SDEM009)) + 
    geom_bar(width=.5) +
    scale_fill_manual(values=pal2) +
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.x = element_blank())
```

```{r disability_tab, eval=!is.null(data$SDEM009)}

print_frqtable(data$SDEM009) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$SDEM005)) get_label(data$SDEM005)`
```{r trans_history, eval=!is.null(data$SDEM005)}

data %>% 
    filter(!is.na(SDEM005) & hideNA) %>% 
    ggplot(aes(x=SDEM005, fill=SDEM005)) + 
    geom_bar(width=.5) +
    scale_fill_manual(values=pal3) +
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.x = element_blank())
```


```{r trans_history_tab, eval=!is.null(data$SDEM005)}

print_frqtable(data$SDEM005)
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$SDEM006)) get_label(data$SDEM006)`
```{r marital_status, eval=!is.null(data$SDEM006)}

data %>% 
    filter(!is.na(SDEM006) & hideNA) %>% 
    ggplot(aes(x=SDEM006, fill=SDEM006)) + 
    geom_bar(width=.5) + 
    scale_fill_manual(values=pal7) +
    coord_flip() + 
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.y=element_blank())
```

```{r marital_status_tab, eval=!is.null(data$SDEM006)}

print_frqtable(data$SDEM006)
```
<p>&nbsp;</p>
<p>&nbsp;</p>


## Nationality, citizenship, social class

### `r if (!is.null(data$SDEM002)) get_label(data$SDEM002)`
```{r ethnicity, eval=!is.null(data$SDEM002)}

data %>% 
    filter(!is.na(SDEM002) & hideNA) %>% 
    ggplot(aes(x=SDEM002, fill=SDEM002)) + 
    geom_bar(width=.5) +
    scale_fill_manual(values=pal3) +
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.x = element_blank())
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$SDEM012)) get_label(data$SDEM012)`
```{r nationality, eval=!is.null(data$SDEM012)}

data %>% 
    filter(!is.na(SDEM012) & hideNA) %>% 
    ggplot(aes(x=SDEM012)) + 
    geom_bar(width=.5) + 
    coord_flip() + 
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.y=element_blank())
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$SDEM013)) get_label(data$SDEM013)`
```{r country_citizen, eval=!is.null(data$SDEM013)}

data %>% 
   filter(!is.na(SDEM013) & hideNA) %>% 
    ggplot(aes(x=SDEM013)) + 
    geom_bar(width=.5) + 
    coord_flip() + 
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.y=element_blank())
```
<p>&nbsp;</p>
<p>&nbsp;</p>



### `r if (!is.null(data$SDEM016)) get_label(data$SDEM016)`
```{r high_qual, eval=!is.null(data$SDEM016), fig.width=10, fig.height=5}

data %>% 
    filter(!is.na(SDEM016) & hideNA) %>% 
    ggplot(aes(x=SDEM016, fill=SDEM016)) + 
    geom_bar(width=.5) + 
    coord_flip() +
    labs(y="Total count") +
    guides(fill=F) + 
    theme_light() +
    theme(axis.title.y=element_blank())
```

```{r high_qual_tab, eval=!is.null(data$SDEM016)}

print_frqtable(data$SDEM016)
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$SDEM017)) get_label(data$SDEM017)`
```{r high_qual_p1, eval=!is.null(data$SDEM017), fig.width=10, fig.height=5}

data %>% 
    filter(!is.na(SDEM017) & hideNA) %>% 
    ggplot(aes(x=SDEM017, fill=SDEM017)) + 
    geom_bar(width=.5) + 
    coord_flip() +
    labs(y="Total count") +
    guides(fill=F) + 
    theme_light() +
    theme(axis.title.y=element_blank())
```

```{r high_qual_p1_tab, eval=!is.null(data$SDEM017)}

print_frqtable(data$SDEM017)
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$SDEM018)) get_label(data$SDEM018)`
```{r high_qual_p2, eval=!is.null(data$SDEM018), fig.width=10, fig.height=5}

data %>% 
    filter(!is.na(SDEM018) & hideNA) %>% 
    ggplot(aes(x=SDEM018, fill=SDEM018)) + 
    geom_bar(width=.5) + 
    coord_flip() +
    labs(y="Total count") +
    guides(fill=F) + 
    theme_light() +
    theme(axis.title.y=element_blank())
```

```{r high_qual_p2_tab, eval=!is.null(data$SDEM018)}

print_frqtable(data$SDEM018) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>















