# (PART) Part - Descriptive Statistics {-}


# Socio-demographics


## Core demographics: age, gender, ...

### `r varlabel("SDEM001")`

```{r year_born, eval=varexists("SDEM001")}

data %>% 
    mutate(age = SDEM001) %>% 
    filter(!is.na(age)) %>% 
    ggplot(aes(x=SDEM001)) + 
    geom_bar()+ 
    labs(title="") +
    theme_light() +
    theme(axis.title.x = element_blank())

```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r varlabel("SDEM004")`
```{r gender, eval=varexists("SDEM004"), fig.align='center'}

data %>% 
    filter(!is.na(SDEM004) & hideNA) %>% 
    ggplot(aes(x=SDEM004, fill=SDEM004)) + 
    geom_bar(width=.5) +
    scale_fill_brewer(palette="Set1") +
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.x = element_blank())
```

<p>&nbsp;</p>

```{r gender_tab, eval=varexists("SDEM004")}

print_frqtable(data$SDEM004)
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r varlabel("SDEM007")`
```{r sex_orientation, eval=varexists("SDEM007")}

data %>% 
    filter(!is.na(SDEM007) & hideNA) %>% 
    ggplot(aes(x=SDEM007, fill=SDEM007)) + 
    geom_bar(width=.5) +
    scale_fill_brewer(palette="Set1") +
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.x = element_blank())
```



```{r sex_orientation_tab, eval=varexists("SDEM007")}

print_frqtable(data$SDEM007) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r varlabel("SDEM009")`

```{r disability, eval=varexists("SDEM009")}

data %>% 
    filter(!is.na(SDEM009) & hideNA) %>% 
    ggplot(aes(x=SDEM009, fill=SDEM009)) + 
    geom_bar(width=.5) +
    scale_fill_brewer(palette="Set1") +
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.x = element_blank())
```

```{r disability_tab, eval=varexists("SDEM009")}

print_frqtable(data$SDEM009) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r varlabel("SDEM005")`
```{r trans_history, eval=varexists("SDEM005")}

data %>% 
    filter(!is.na(SDEM005) & hideNA) %>% 
    ggplot(aes(x=SDEM005, fill=SDEM005)) + 
    geom_bar(width=.5) +
    scale_fill_brewer(palette="Set1") +
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.x = element_blank())
```


```{r trans_history_tab, eval=varexists("SDEM005")}

print_frqtable(data$SDEM005)
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r varlabel("SDEM006")`
```{r marital_status, eval=varexists("SDEM006")}

data %>% 
    filter(!is.na(SDEM006) & hideNA) %>% 
    ggplot(aes(x=SDEM006, fill=SDEM006)) + 
    geom_bar(width=.5) + 
    scale_fill_brewer(palette="Set1") +
    coord_flip() + 
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.y=element_blank())
```

```{r marital_status_tab, eval=varexists("SDEM006")}

print_frqtable(data$SDEM006)
```
<p>&nbsp;</p>
<p>&nbsp;</p>


## Nationality, citizenship, social class

### `r varlabel("SDEM002")`
```{r ethnicity, eval=varexists("SDEM002")}

data %>% 
    filter(!is.na(SDEM002) & hideNA) %>% 
    ggplot(aes(x=SDEM002, fill=SDEM002)) + 
    geom_bar(width=.5) +
    scale_fill_brewer(palette="Set1") +
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.x = element_blank())
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r varlabel("SDEM012")`
```{r nationality, eval=varexists("SDEM012")}

data %>% 
    filter(!is.na(SDEM012) & hideNA) %>% 
    ggplot(aes(x=SDEM012)) + 
    geom_bar(width=.5) + 
    coord_flip() + 
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.y=element_blank())
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r varlabel("SDEM013")`
```{r country_citizen, eval=varexists("SDEM013")}

data %>% 
   filter(!is.na(SDEM013) & hideNA) %>% 
    ggplot(aes(x=SDEM013)) + 
    geom_bar(width=.5) + 
    coord_flip() + 
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.y=element_blank())
```
<p>&nbsp;</p>
<p>&nbsp;</p>



### `r varlabel("SDEM016")`
```{r high_qual, eval=varexists("SDEM016"), fig.width=10, fig.height=5}

data %>% 
    filter(!is.na(SDEM016) & hideNA) %>% 
    ggplot(aes(x=SDEM016, fill=SDEM016)) + 
    geom_bar(width=.5) + 
    coord_flip() +
    labs(y="Total count") +
    guides(fill=F) + 
    theme_light() +
    theme(axis.title.y=element_blank())
```

```{r high_qual_tab, eval=varexists("SDEM016")}

print_frqtable(data$SDEM016)
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r varlabel("SDEM017")`
```{r high_qual_p1, eval=varexists("SDEM017"), fig.width=10, fig.height=5}

data %>% 
    filter(!is.na(SDEM017) & hideNA) %>% 
    ggplot(aes(x=SDEM017, fill=SDEM017)) + 
    geom_bar(width=.5) + 
    coord_flip() +
    labs(y="Total count") +
    guides(fill=F) + 
    theme_light() +
    theme(axis.title.y=element_blank())
```

```{r high_qual_p1_tab, eval=varexists("SDEM017")}

print_frqtable(data$SDEM017)
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r varlabel("SDEM018")`
```{r high_qual_p2, eval=varexists("SDEM018"), fig.width=10, fig.height=5}

data %>% 
    filter(!is.na(SDEM018) & hideNA) %>% 
    ggplot(aes(x=SDEM018, fill=SDEM018)) + 
    geom_bar(width=.5) + 
    coord_flip() +
    labs(y="Total count") +
    guides(fill=F) + 
    theme_light() +
    theme(axis.title.y=element_blank())
```

```{r high_qual_p2_tab, eval=varexists("SDEM018")}

print_frqtable(data$SDEM018) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>

