# Socio-demographics


## Sample description: Socio-demographic variables


### `r var_toplabel("SDEM001")` `r if(lsVarCode) "(SDEM001)"`
<p>&nbsp;</p>


```{r eval=var_exists("SDEM001"), fig.cap=get_caption("SDEM001")}

################################################
# Year born
################################################

df.geam %>%  
    mutate(Born = SDEM001) %>% 
    filter(!is.na(age)) %>% 
    ggplot(aes(x=SDEM001)) + 
    geom_bar()+ 
    labs(title="") +
    theme_light() +
    theme(axis.title.x = element_blank())

```


<p>&nbsp;</p>


```{r fig.cap=get_i18n("Age")}
df.geam %>% 
    print_barplot(age_i10)
```


<p>&nbsp;</p>


```{r eval=var_exists("SDEM004")}
df.geam %>%
  print_frqtable("age_i10", lsort.frq="none")

```


\newpage
  
  
  
  
  
### `r var_toplabel("SDEM004")`  `r if(lsVarCode) "(SDEM004)"`
<p>&nbsp;</p>


```{r eval=var_exists("SDEM004"), fig.cap=get_caption("SDEM004")}

################################################
# Gender
################################################

df.geam %>% 
    print_barplot(SDEM004)
```


<p>&nbsp;</p>


```{r eval=var_exists("SDEM004")}
df.geam %>% 
    print_frqtable("SDEM004")
```


\newpage

   
   
   
   
### `r var_toplabel("SDEM007")`  `r if(lsVarCode) "(SDEM007)"`
<p>&nbsp;</p>
 
  
```{r eval=var_exists("SDEM007"), fig.cap=get_caption("SDEM007")}

################################################
# Sexual orientation 
################################################

df.geam %>% 
    print_barplot(SDEM007, xlangle = 60, lwidth=25)
```


<p>&nbsp;</p>


```{r eval=var_exists("SDEM007")}
df.geam %>% 
    print_frqtable("SDEM007") 
```


\newpage
  
  
  
  
  
### `r var_toplabel("SDEM009")`  `r if(lsVarCode) "(SDEM009)"`
<p>&nbsp;</p>
 
  
```{r eval=var_exists("SDEM009"), fig.cap=get_caption("SDEM009")}

################################################
# Disability 
################################################

df.geam %>% 
    print_barplot(SDEM009)
```


<p>&nbsp;</p>


```{r eval=var_exists("SDEM009")}
df.geam %>% 
    print_frqtable("SDEM009") 
```


    
\newpage
  
  
  
  
  
### `r var_toplabel("SDEM005")`  `r if(lsVarCode) "(SDEM005)"`
<p>&nbsp;</p>
 
  
```{r eval=var_exists("SDEM005"), fig.cap=get_caption("SDEM005")}

################################################
# Trans history 
################################################

df.geam %>%  
    print_barplot(SDEM005)
```


<p>&nbsp;</p>


```{r eval=var_exists("SDEM005")}
df.geam %>% 
    print_frqtable("SDEM005")
```


     
\newpage
  
  
  
  
  
### `r var_toplabel("SDEM006")`  `r if(lsVarCode) "(SDEM006)"`
<p>&nbsp;</p>
 
  
```{r eval=var_exists("SDEM006"), fig.cap=get_caption("SDEM006")}

################################################
# Marital status 
################################################

df.geam %>%  
    print_barplot(SDEM006, xlangle = 60, lwidth=30)
```


<p>&nbsp;</p>


```{r eval=var_exists("SDEM006")}
df.geam %>% 
    print_frqtable("SDEM006")
```


\newpage
  
  
  
  
  
## Nationality, citizenship, social class
<p>&nbsp;</p>

### `r var_toplabel("SDEM002")`  `r if(lsVarCode) "(SDEM002)"`
<p>&nbsp;</p>
 
  
```{r eval=var_exists("SDEM002"), fig.cap=get_caption("SDEM002")}

################################################
# Ethnicity Mintority Group 
################################################

df.geam %>%  
    print_barplot(SDEM002)
```


<p>&nbsp;</p>


```{r eval=var_exists("SDEM002")}
df.geam %>% 
    print_frqtable("SDEM002")
```



\newpage
  
  
  
  
  
### `r var_toplabel("SDEM012")`  `r if(lsVarCode) "(SDEM012)"`
<p>&nbsp;</p>
Note: to keep the chart readable, only nationalities which have at least 2 responses are included. 
  

```{r, eval=var_exists("SDEM012"), fig.cap=get_caption("SDEM012")}

################################################
# Country of birth  
################################################

df.geam %>% 
  mutate(SDEM012_minfrq = forcats::fct_lump_min(SDEM012, min=2, other_level = "Other")) %>%
  print_barplot(SDEM012_minfrq)
```


<p>&nbsp;</p>


```{r eval=var_exists("SDEM012")}

# df.geam %>%
#   mutate(SDEM012_minfrq = forcats::fct_lump_min(SDEM012, min=1, other_level = "Other")) %>% 
#   print_frqtable("SDEM012_minfrq")

df.geam %>% 
  print_frqtable("SDEM012", min.frq=1)

```


\newpage




  
### `r var_toplabel("SDEM013")`  `r if(lsVarCode) "(SDEM013)"`
<p>&nbsp;</p>
Note: to keep the chart readable, only nationalities which have at least 2 responses are included. 


```{r eval=var_exists("SDEM013"), fig.cap=get_caption("SDEM013")}

################################################
# Citizenship  
################################################

# Only include nationalities that have at least 2 responses

df.geam %>% 
  mutate(SDEM013_minfrq = forcats::fct_lump_min(SDEM013, min=2, other_level = "Other")) %>%
  print_barplot(SDEM013_minfrq)
```


<p>&nbsp;</p>


```{r eval=var_exists("SDEM013")}

# df.geam %>%
#   mutate(SDEM013_minfrq = forcats::fct_lump_min(SDEM013, min=1, other_level = "Other")) %>% 
#   print_frqtable("SDEM013_minfrq")

df.geam %>% 
  print_frqtable("SDEM013", min.frq=1)

```

\newpage
  
  
  
  
  
### `r var_toplabel("SDEM016")`  `r if(lsVarCode) "(SDEM016)"`
<p>&nbsp;</p>
 
  
```{r eval=var_exists("SDEM016"), fig.width=7, fig.cap=get_caption("SDEM016")}

################################################
# Highest Qualification
################################################

df.geam %>%  
    print_barplot(SDEM016, lwidth=20, xlangle=60)
```


<p>&nbsp;</p>


```{r eval=var_exists("SDEM016")}
df.geam %>% 
    print_frqtable("SDEM016")
```
 
\newpage




  
### `r var_toplabel("SDEM017")`  `r if(lsVarCode) "(SDEM017)"`
<p>&nbsp;</p>
 
  
```{r eval=var_exists("SDEM017"), fig.width=7, fig.cap=get_caption("SDEM017")}

################################################
# Highest Qualification Parent 1 
################################################

df.geam %>%  
    print_barplot(SDEM017, lwidth=20, xlangle=60)
```


<p>&nbsp;</p>


```{r eval=var_exists("SDEM017")}
df.geam %>% 
    print_frqtable("SDEM017")
```


\newpage
  
  
  
  
  
### `r var_toplabel("SDEM018")`  `r if(lsVarCode) "(SDEM018)"`
<p>&nbsp;</p>
 
  
```{r eval=var_exists("SDEM018"), fig.width=7, fig.cap=get_caption("SDEM018")}

################################################
# Highest Qualification Parent 2
################################################

df.geam %>%  
    print_barplot(SDEM018, lwidth=20, xlangle=60)
```


<p>&nbsp;</p>


```{r eval=var_exists("SDEM018")}
df.geam %>% 
    print_frqtable("SDEM018") 
```


\newpage
  