## Parental Leave

Includes questions 22-31, codes: WCWI011a, WCWI011b, WCWI014, WCWI015, WCWI016, WCWI017, WCWI018, WCWI020, WCWI021, WCWI023. 


### `r if (!is.null(data$WCWI011a)) get_label(data$WCWI011a)`

```{r takenparental, eval=!is.null(data$WCWI011a) }

# ever taken parental leave 

data %>% 
    filter(!is.na(WCWI011a) & hideNA) %>% 
    ggplot(aes(x=WCWI011a)) + 
    geom_bar()+ 
    labs(title="") +
    theme_light() +
    theme(axis.title.x = element_blank())
```

```{r eval=!is.null(data$WCWI011a)}
print_frqtable(data$WCWI011a) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>



### `r if (!is.null(data$WCWI011b_SQ001)) attr(data$WCWI011b_SQ001, "question_label")`
```{r eval=!is.null(data$WCWI011b_SQ001), fig.height=3, fig.width=10}
data %>%
  select(starts_with("WCWI011b_SQ0")) %>%
  plot_likert(geom.colors=pal6, values="show", show.prc.sign=T, cat.neutral = NULL) + 
  theme_light()
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$WCWI014)) get_label(data$WCWI014)`
```{r eval=!is.null(data$WCWI014)}
data %>% 
    filter(!is.na(WCWI014) & hideNA) %>% 
    ggplot(aes(x=WCWI014)) + 
    geom_bar()+ 
    labs(y="Total count") +
    theme_light() +
    theme(axis.title.x = element_blank())
```

```{r eval=!is.null(data$WCWI014)}
print_frqtable(data$WCWI014) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$WCWI015)) get_label(data$WCWI015)`
```{r eval=!is.null(data$WCWI015), fig.width=10}
data %>% 
    filter(!is.na(WCWI015) & hideNA) %>% 
    ggplot(aes(x=WCWI015, fill=WCWI015)) + 
    geom_bar() + 
    scale_fill_manual(values=pal6) +
    coord_flip() + 
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.y=element_blank())
```

```{r eval=!is.null(data$WCWI015)}
print_frqtable(data$WCWI015) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$WCWI016_SQ001)) attr(data$WCWI016_SQ001, "question_label")`

```{r eval=!is.null(data$WCWI016_SQ001), fig.height=8, fig.width=10}

# Indicate availability of parental leave  

data %>%
  select(starts_with("WCWI016_SQ0")) %>%
  plot_likert(geom.colors=pal6, values="show", show.prc.sign=T, catcount = 4, cat.neutral = NULL) + 
  theme_light() 

```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$WCWI018_SQ001)) attr(data$WCWI018_SQ001, "question_label")`

```{r eval=!is.null(data$WCWI018_SQ001), fig.height=8, fig.width=10}

# Helpfullness preparing leave

data %>%
  select(starts_with("WCWI018_SQ0")) %>%
  plot_likert(geom.colors=pal6, values="show", show.prc.sign=T, catcount = 6, cat.neutral = NULL) + 
  theme_light()

```
<p>&nbsp;</p>
<p>&nbsp;</p>



### `r if (!is.null(data$WCWI020)) get_label(data$WCWI020)`
```{r eval=!is.null(data$WCWI020), fig.width=10}

# Most recent parental leave: preparedness

data %>% 
    filter(!is.na(WCWI020) & hideNA) %>% 
    ggplot(aes(x=WCWI020, fill=WCWI020)) + 
    geom_bar() + 
    scale_fill_manual(values=pal6) +
    coord_flip() + 
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.y=element_blank())
```

```{r eval=!is.null(data$WCWI020)}
print_frqtable(data$WCWI020)
```
<p>&nbsp;</p>
<p>&nbsp;</p>



### `r if (!is.null(data$WCWI021_SQ001)) attr(data$WCWI021_SQ001, "question_label")`

```{r eval=!is.null(data$WCWI021_SQ001), fig.height=10, fig.width=10}

# Helpfullness preparing return

data %>%
  select(starts_with("WCWI021_SQ0")) %>%
  plot_likert(geom.colors=pal6, values="show", show.prc.sign=T, catcount = 4, cat.neutral = NULL) + 
  theme_light()

```
<p>&nbsp;</p>
<p>&nbsp;</p>
