# Working Conditions 

## About your current job


### `r var_toplabel("WCJC001")`  `r if(lsVarCode) "(WCJC001)" `
<p>&nbsp;</p>


```{r eval=var_exists("WCJC001"), fig.cap=get_caption("WCJC001") }

################################################
# your postition
################################################

df.geam %>% 
    print_barplot(WCJC001, lwidth=20)
```


<p>&nbsp;</p>


```{r eval=var_exists("WCJC001")}
df.geam %>% 
    print_frqtable("WCJC001") 
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC001", "SDEM004.bin")), fig.cap=get_caption("WCJC001", "SDEM004.bin")}
df.geam %>% 
  print_xbarplot("SDEM004.bin", "WCJC001", legpos = "right", legdir = "vertical", ltitle=F, lwidth = 10)

```
    
    
<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC001", "SDEM004.bin"))}
df.geam %>% 
    print_xtable("WCJC001", "SDEM004.bin")

```    
\newpage
  



### `r var_toplabel("WCJC003")`  `r if(lsVarCode) "(WCJC003)" `
<p>&nbsp;</p>


```{r eval=var_exists("WCJC003"), fig.width=10, fig.height=10, , fig.cap=get_caption("WCJC003")}

################################################
# academic field
################################################

df.geam %>% 
    print_barplot(WCJC003, lwidth=20)
```
  
    
\newpage



  
### `r var_toplabel("WCJC003PL")`  `r if(lsVarCode) "(WCJC003PL)" `
<p>&nbsp;</p>


```{r eval=var_exists("WCJC003PL")}

################################################
# academic field PL
################################################

# df.geam %>% 
#     print_barplot(WCJC003PL, turn90=T, labelwidth = 30)

```


<p>&nbsp;</p>


```{r eval=var_exists("WCJC003PL")}
df.geam %>% 
    print_frqtable("WCJC003PL") 
```


\newpage



  
### `r var_toplabel("WCJC004")`  `r if(lsVarCode) "(WCJC004)" `
<p>&nbsp;</p>


```{r eval=var_exists("WCJC004"), fig.height=7, fig.cap=get_caption("WCJC004")}

################################################
# your post
################################################

# df.geam %>%
#     print_barplot(WCJC004, lwidth = 20, coords90=T)
```


<p>&nbsp;</p>


```{r eval=var_exists("WCJC004")}
df.geam %>% 
    print_frqtable("WCJC004")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC004", "SDEM004.bin")), fig.cap=get_caption("WCJC004", "SDEM004.bin")}
# df.geam %>% 
#   print_xbarplot("WCJC004", "SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC004", "SDEM004.bin"))}
df.geam %>% 
    print_xtable("WCJC004", "SDEM004.bin")
```


\newpage





### `r var_toplabel("manager")`  `r if(lsVarCode) "(manager)" `
<p>&nbsp;</p>


```{r eval=var_exists("manager"), fig.cap=get_caption("manager")}

################################################
# Leadership function 
################################################

df.geam %>%
    print_barplot(manager)
```


<p>&nbsp;</p>


```{r eval=var_exists("manager")}
df.geam %>% 
    print_frqtable("manager")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("manager", "SDEM004.bin")), fig.cap=get_caption("manager", "SDEM004.bin")}
df.geam %>%
  print_xbarplot("SDEM004.bin", "manager", legpos = "right", legdir = "vertical", ltitle=F)
```
   
   
<p>&nbsp;</p>


```{r eval=var_exists(c("manager", "SDEM004.bin"))}
df.geam %>% 
    print_xtable("manager", "SDEM004.bin")
```
   
    
\newpage  





### `r var_toplabel("WCJC005")`  `r if(lsVarCode) "(WCJC005)" `
<p>&nbsp;</p>


```{r}
summary(df.geam$WCJC005)
```
<p>&nbsp;</p>


```{r eval=var_exists("WCJC005_i1000"), fig.cap=get_caption("WCJC005")}

################################################
# net salary 
################################################

df.geam %>% 
  print_barplot(WCJC005_i1000, xlangle=60)
```


<p>&nbsp;</p>


```{r eval=var_exists("WCJC005_i1000")}
df.geam %>% 
  print_frqtable("WCJC005_i1000", lsort.frq="none") 
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC005_i1000", "SDEM004.bin"))}
# df.geam %>% 
#   print_xbarplot("WCJC005_i1000", "SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC005_i1000", "SDEM004.bin"))}
df.geam %>% 
    print_xtable("WCJC005_i1000", "SDEM004.bin")
```


  
\newpage





  
### `r var_toplabel("WCJ005a")`  `r if(lsVarCode) "(WCJ005a)" `
<p>&nbsp;</p>


```{r eval=var_exists("WCJ005a"), fig.cap=get_caption("WCJ005a")}

################################################
# Received a bonus
################################################

df.geam %>%
    print_barplot(WCJ005a)
```


<p>&nbsp;</p>


```{r eval=var_exists("WCJ005a")}
df.geam %>% 
    print_frqtable("WCJ005a") 
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJ005a", "SDEM004.bin")), fig.cap=get_caption("WCJ005a", "SDEM004.bin")}
df.geam %>% 
  print_xbarplot("SDEM004.bin", "WCJ005a", legpos = "right", legdir = "vertical", ltitle=F)
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJ005a", "SDEM004.bin"))}
df.geam %>% 
    print_xtable("WCJ005a", "SDEM004.bin")
```

    
\newpage
  
  
  
  

### `r var_toplabel("WCJC008")`  `r if(lsVarCode) "(WCJC008)" `
<p>&nbsp;</p>


```{r eval=var_exists("WCJC008"), fig.cap=get_caption("WCJC008")}

################################################
# Years employed
################################################

df.geam %>% 
    print_barplot(WCJC008, xlangle = 60)
```


<p>&nbsp;</p>


```{r eval=var_exists("WCJC008")}
df.geam %>% 
    print_frqtable("WCJC008") 
```


\newpage



  
### `r var_toplabel("WCJC010")`  `r if(lsVarCode) "(WCJC010)" `
<p>&nbsp;</p>


```{r val=var_exists("WCJC010"),fig.cap=get_caption("WCJC010") }

################################################
# Full or part time 
################################################

df.geam %>%
    print_barplot(WCJC010)
```


<p>&nbsp;</p>


```{r eval=var_exists("WCJC010")}
df.geam %>% 
    print_frqtable("WCJC010") 
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC010", "SDEM004.bin")), fig.cap=get_caption("WCJC010", "SDEM004.bin")}
df.geam %>% 
  print_xbarplot("SDEM004.bin", "WCJC010", legpos = "right", legdir = "vertical", ltitle=F)
```
  
  
<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC010", "SDEM004.bin"))}
df.geam %>% 
    print_xtable("WCJC010", "SDEM004.bin")
```


\newpage
  
  
  
  
  
### `r var_toplabel("WCJC011")` `r if(lsVarCode) "(WCJC011)" `
<p>&nbsp;</p>


```{r eval=var_exists("WCJC011"), fig.cap=get_caption("WCJC011")}

################################################
# Type of contract: part time or fixed
################################################

df.geam %>% 
    print_barplot(WCJC011)
```


<p>&nbsp;</p>


```{r eval=var_exists("WCJC011")}
df.geam %>% 
    print_frqtable("WCJC011")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC011", "SDEM004.bin")), fig.cap=get_caption("WCJC011", "SDEM004.bin")}
df.geam %>% 
  print_xbarplot("SDEM004.bin","WCJC011", legpos = "right", legdir = "vertical", ltitle=F)
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC011", "SDEM004.bin"))}
df.geam %>% 
    print_xtable("WCJC011", "SDEM004.bin")
```



\newpage





### `r var_toplabel("G01Q82")`  `r if(lsVarCode) "(G01Q82)" `
<p>&nbsp;</p>


```{r eval=var_exists("G01Q82") }

################################################
# Unit employed
################################################

# df.geam %>% 
#     print_barplot(G01Q82, coords90 =T, lwidth = 15) 
```


<p>&nbsp;</p>


```{r eval=var_exists("G01Q82")}
df.geam %>% 
    print_frqtable("G01Q82")
```
  
\newpage
  
