# Working Conditions 

## About your current job

Includes questions 2-8, codes: WCJC001, WCJC003, WCJC004, WCJC005, WCJ005a, WCJC010, WCJC011. 


### `r if (!is.null(data$WCJC001)) get_label(data$WCJC001)`

```{r your_position, eval=!is.null(data$WCJC001) }
data %>% 
    filter(!is.na(WCJC001) & hideNA) %>% 
    ggplot(aes(x=WCJC001)) + 
    geom_bar()+ 
    labs(y="Total count") +
    theme_light() +
    theme(axis.title.x = element_blank())
```


```{r your_position_tab, eval=!is.null(data$WCJC001)}

print_frqtable(data$WCJC001) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$WCJC003)) get_label(data$WCJC003)`

```{r academic_field, eval=!is.null(data$WCJC003), fig.width=10, fig.height=10}
data %>% 
    filter(!is.na(WCJC003) & hideNA) %>% 
    ggplot(aes(x=WCJC003, fill=WCJC003)) + 
    geom_bar() + 
    coord_flip() + 
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.y=element_blank())
```

```{r academic_field_tab, eval=!is.null(data$WCJC004)}

print_frqtable(data$WCJC003) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$WCJC004)) get_label(data$WCJC004)`
```{r your_post, eval=!is.null(data$WCJC004), fig.width=8, fig.height=4}
data %>% 
    filter(!is.na(WCJC004) & hideNA) %>% 
    ggplot(aes(x=WCJC004, fill=WCJC004)) + 
    geom_bar() + 
    coord_flip() + 
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.y=element_blank())
```

```{r your_post_tab, eval=!is.null(data$WCJC004)}
print_frqtable(data$WCJC004)
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$WCJC005)) get_label(data$WCJC005)`

```{r net_salary, eval=!is.null(data$WCJC005)}
data %>% 
    ggplot(aes(x=WCJC005)) + 
    geom_bar()+ 
    labs(y="Total count") +
    theme_light() +
    theme(axis.title.x = element_blank())

```

```{r}
summary(data$WCJC005)
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$WCJ005a)) get_label(data$WCJ005a)`

```{r bonus, eval=!is.null(data$WCJ005a) }
data %>% 
    filter(!is.na(WCJ005a) & hideNA) %>% 
    ggplot(aes(x=WCJ005a)) + 
    geom_bar()+ 
    labs(y="Total count") +
    theme_light() +
    theme(axis.title.x = element_blank())
```

```{r bonus_tab, eval=!is.null(data$WCJ005a)}
print_frqtable(data$WCJ005) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$WCJC010)) get_label(data$WCJC010)`

```{r fullpart_time, eval=!is.null(data$WCJC010) }
data %>% 
    filter(!is.na(WCJC010) & hideNA) %>% 
    ggplot(aes(x=WCJC010)) + 
    geom_bar()+ 
    labs(y="Total count") +
    theme_light() +
    theme(axis.title.x = element_blank())
```

```{r fullpart_time_tab, eval=!is.null(data$WCJC010)}
print_frqtable(data$WCJC010) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>



### `r if (!is.null(data$WCJC011)) get_label(data$WCJC011)`

```{r temp_fixed, eval=!is.null(data$WCJC011) }
data %>% 
    filter(!is.na(WCJC011) & hideNA) %>% 
    ggplot(aes(x=WCJC011)) + 
    geom_bar()+ 
    labs(y="Total count") +
    theme_light() +
    theme(axis.title.x = element_blank())
```

```{r temp_fixed_tab, eval=!is.null(data$WCJC011)}
print_frqtable(data$WCJC011)
```
<p>&nbsp;</p>
<p>&nbsp;</p>

