## Work-life Balance

Includes questions 14-21, codes: WCWI006, WCWI008, WCWI009, WCWI010, WCWI005, EWCS89JobSatisfact8, EWCS36WorkIntensity2, WorkFamConfISSP 


### `r varlabel("WCWI006")`

```{r primecare, eval=varexists("WCWI006") }

data %>% 
    filter(!is.na(WCWI006) & hideNA) %>% 
    ggplot(aes(x=WCWI006)) + 
    geom_bar()+ 
    labs(title="") +
    theme_light() +
    theme(axis.title.x = element_blank())
```

```{r primecare_tab, eval=varexists("WCWI006")}
print_frqtable(data$WCWI006) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r varlabel("WCWI008")`
```{r guardian18, eval=varexists("WCWI008") }

# parent or legal guardian for children 18 years or younger

data %>% 
    filter(!is.na(WCWI008) & hideNA) %>% 
    ggplot(aes(x=WCWI008)) + 
    geom_bar()+ 
    labs(title="") +
    theme_light() +
    theme(axis.title.x = element_blank())
```

```{r guardian18_tab, eval=varexists("WCWI008")}
print_frqtable(data$WCWI008) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>



### `r varlabel("WCWI010")`
```{r single_guardian18, eval=varexists("WCWI008") }

# parent or legal guardian for children 18 years or younger

data %>% 
    filter(!is.na(WCWI010) & hideNA) %>% 
    ggplot(aes(x=WCWI010)) + 
    geom_bar()+ 
    labs(title="") +
    theme_light() +
    theme(axis.title.x = element_blank())
```

```{r single_guardian18_tab, eval=varexists("WCWI010")}
print_frqtable(data$WCWI010) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>



### `r varlabel("WCWI009")`
```{r nr_children, eval=varexists("WCWI009"), fig.width=8, fig.height=4}
data %>% 
    filter(!is.na(WCJC014) & hideNA) %>% 
    ggplot(aes(x=WCWI009, fill=WCWI009)) + 
    geom_bar() + 
    scale_fill_brewer(palette="Set1") +
    coord_flip() + 
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.y=element_blank())
```

```{r nr_children_tab, eval=varexists("WCWI009")}
print_frqtable(data$WCWI009) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r varlabel("WCWI005_SQ001")`

```{r eval=varexists("WCWI005_SQ001"), fig.height=4, fig.width=10}

data %>%
  select(starts_with("WCWI005_SQ0")) %>%
  plot_likert(geom.colors="Set1", values="show", show.prc.sign=T, catcount = 4, cat.neutral = NULL) + 
  #theme_sjplot(base_size = 20, base_family = "")
  #font_size(title=10, axis_title.x=10, axis_title.y=12, labels.x=8, labels.y=12)
  theme_light() +
  theme(axis.text.y = element_text(size=11))

```
<p>&nbsp;</p>
<p>&nbsp;</p>



### `r varlabel("EWCS89JobSatisfact8_SQ001")`

```{r eval=varexists("EWCS89JobSatisfact8_SQ001"), fig.height=8, fig.width=10}
data %>%
  select(starts_with("EWCS89JobSatisfact8_SQ0")) %>%
  plot_likert(geom.colors="Set1", values="show", show.prc.sign=T, catcount = 4, cat.neutral = 3) + 
  theme_light()

```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r varlabel("EWCS36WorkIntensity2_SQ001")`

```{r eval=varexists("EWCS36WorkIntensity2_SQ001"), fig.height=3, fig.width=10}
data %>%
  select(starts_with("EWCS36WorkIntensity2_SQ0")) %>%
  plot_likert(geom.colors="Set1", values="show", show.prc.sign=T, catcount = 4, cat.neutral = NULL) + 
  theme_light()
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r varlabel("WorkFamConfISSP_SQ001")`

```{r eval=varexists("WorkFamConfISSP_SQ001"), fig.height=4, fig.width=10}
data %>%
  select(starts_with("WorkFamConfISSP_SQ0")) %>%
  plot_likert(geom.colors="Set1", values="show", show.prc.sign=T, catcount = 4, cat.neutral = NULL) + 
  theme_light()

```
<p>&nbsp;</p>
<p>&nbsp;</p>



### `r varlabel("Covid_SQ01")`

```{r eval=varexists("Covid_SQ01"), fig.height=12, fig.width=10}
data %>%
  select(starts_with("Covid_SQ")) %>%
  plot_likert(geom.colors="Set1", values="show", show.prc.sign=T, catcount = 4, cat.neutral = NULL) + 
  theme_light()

```





















