## Work-life Balance


### `r var_toplabel("WCWI006")`  `r if(lsVarCode) "(WCWI006)" `
<p>&nbsp;</p>


```{r eval=var_exists("WCWI006"), fig.cap=get_caption("WCWI006") }

################################################
# Are you primary carer or assistant for an adult
################################################

df.geam %>%
    print_barplot(WCWI006)
```


<p>&nbsp;</p>


```{r eval=var_exists("WCWI006")}
df.geam %>% 
    print_frqtable("WCWI006") 
```


\newpage 


```{r eval=var_exists(c("WCWI006", "SDEM004.bin"))}
df.geam %>% 
    print_xtable("WCWI006", "SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCWI006", "SDEM004.bin")), fig.cap=get_caption("WCWI006", "SDEM004.bin")}
df.geam %>% 
  print_xbarplot("SDEM004.bin", "WCWI006", legpos = "right", legdir = "vertical", ltitle=F, lwidth = 15)
```
  
\newpage
  



### `r var_toplabel("WCWI008")`  `r if(lsVarCode) "(WCWI008)" `
<p>&nbsp;</p>


```{r eval=var_exists("WCWI008"), fig.cap=get_caption("WCWI008") }

################################################
# Parent or legal guardian of any children
################################################

df.geam %>%
    print_barplot(WCWI008)
```


<p>&nbsp;</p>


```{r eval=var_exists("WCWI008")}
df.geam %>% 
    print_frqtable("WCWI008") 
```


\newpage 


```{r eval=var_exists(c("WCWI008", "SDEM004.bin"))}
df.geam %>% 
    print_xtable("WCWI008", "SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCWI008", "SDEM004.bin")), fig.cap=get_caption("WCWI008", "SDEM004.bin")}
df.geam %>% 
  print_xbarplot("SDEM004.bin","WCWI008", legpos = "right", legdir = "vertical", ltitle=F, lwidth = 15)
```
  
\newpage




### `r var_toplabel("WCWI010")`  `r if(lsVarCode) "(WCWI010)" `
<p>&nbsp;</p>


```{r eval=var_exists("WCWI010"), fig.cap=get_caption("WCWI010") }

################################################
# Are you single parent
################################################

df.geam %>%
    print_barplot(WCWI010)
```


<p>&nbsp;</p>


```{r eval=var_exists("WCWI010")}
df.geam %>% 
    print_frqtable("WCWI010") 
```


\newpage 


```{r eval=var_exists(c("WCWI010", "SDEM004.bin"))}
df.geam %>% 
    print_xtable("WCWI010", "SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCWI010", "SDEM004.bin")), fig.cap=get_caption("WCWI010", "SDEM004.bin")}
df.geam %>% 
  print_xbarplot("SDEM004.bin", "WCWI010", legpos = "right", legdir = "vertical", ltitle=F, lwidth = 15)
```
  
\newpage





### `r var_toplabel("WCWI009")`  `r if(lsVarCode) "(WCWI009)" `
<p>&nbsp;</p>


```{r eval=var_exists("WCWI009"), fig.cap=get_caption("WCWI009") }

################################################
# How many children
################################################

df.geam %>%
    print_barplot(WCWI009)
```


<p>&nbsp;</p>


```{r eval=var_exists("WCWI009")}
df.geam %>% 
    print_frqtable("WCWI009") 
```
    
\newpage





### `r var_toplabel("WCWI005.SQ001.")`  `r if(lsVarCode) "(WCWI005)" `
<p>&nbsp;</p>


```{r eval=var_exists("WCWI005.SQ001."), fig.height=5.2, fig.cap=get_caption("WCWI005.SQ001.")}

################################################
# Awareness of follwing working options  Parent: WCWI005
################################################

df.geam %>% 
  select(starts_with("WCWI005.SQ")) %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                digits = percdigits,
                geom.size = .4,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        legend.key.width = unit(.4, "cm"),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 12))


```


\newpage 




#### `r var_label("WCWI005.SQ001.")`


```{r eval=exechunk("WCWI005.SQ001."), fig.height=3, fig.cap=get_caption("WCWI005.SQ001.", topl=c(F,T))}

###############
# Ask for time off at a short notice 
###############

df.geam %>%
     print_barplot(WCWI005.SQ001.)

```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC001", "WCWI005.SQ001."))}

# crosstab by role 
df.geam %>% 
    print_xtable("WCWI005.SQ001.","WCJC001")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCWI005.SQ001.", "WCJC001")), fig.cap=get_caption("WCWI005.SQ001.", "WCJC001", c(F,T) )}
df.geam %>% 
  print_xbarplot("WCJC001", "WCWI005.SQ001.", xlangle=0, ltitle=F, legdir = "vertical", legpos = "right", lwidth = 10)
```


\newpage


```{r eval=var_exists(c("SDEM004.bin", "WCWI005.SQ001."))}

# crosstab by gender 
df.geam %>% 
    print_xtable("WCWI005.SQ001.","SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCWI005.SQ001.", "SDEM004.bin")), fig.cap=get_caption("WCWI005.SQ001.", "SDEM004.bin", c(F,T) )}
df.geam %>% 
  print_xbarplot("SDEM004.bin", "WCWI005.SQ001.", legpos = "right", legdir = "vertical", ltitle=F, lwidth = 15)
```

\newpage



#### `r var_label("WCWI005.SQ002.")`


```{r eval=exechunk("WCWI005.SQ002."), fig.height=3, fig.cap=get_caption("WCWI005.SQ002.", topl=c(F,T))}

###############
# Flexibility in hours and days worked
###############

df.geam %>%
    print_barplot(WCWI005.SQ002.)

```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC001", "WCWI005.SQ002."))}

# crosstab by role 
df.geam %>% 
    print_xtable("WCWI005.SQ002.","WCJC001")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCWI005.SQ002.", "WCJC001")), fig.cap=get_caption("WCWI005.SQ002.", "WCJC001", c(F,T) )}
df.geam %>% 
  print_xbarplot("WCJC001", "WCWI005.SQ002.", xlangle=0, ltitle=F, legdir = "vertical", legpos = "right", lwidth = 10)
```


\newpage


```{r eval=var_exists(c("SDEM004.bin", "WCWI005.SQ002."))}

# crosstab by gender 
df.geam %>% 
    print_xtable("WCWI005.SQ002.","SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCWI005.SQ002.", "SDEM004.bin")), fig.cap=get_caption("WCWI005.SQ002.", "SDEM004.bin", c(F,T) )}
df.geam %>% 
  print_xbarplot("SDEM004.bin", "WCWI005.SQ002.", legpos = "right", legdir = "vertical", ltitle=F, lwidth = 15)
```


\newpage




#### `r var_label("WCWI005.SQ003.")`


```{r eval=exechunk("WCWI005.SQ003."), fig.height=3, fig.cap=get_caption("WCWI005.SQ003.", topl=c(F,T))}

###############
# Home based or remote working
###############

df.geam %>%
    print_barplot(WCWI005.SQ003.)

```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC001", "WCWI005.SQ003."))}

# crosstab by role 
df.geam %>% 
    print_xtable("WCWI005.SQ003.","WCJC001")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCWI005.SQ003.", "WCJC001")), fig.cap=get_caption("WCWI005.SQ003.", "WCJC001", c(F,T) )}
df.geam %>% 
  print_xbarplot("WCJC001", "WCWI005.SQ003.", xlangle=0, ltitle=F, legdir = "vertical", legpos = "right", lwidth = 10)
```


\newpage


```{r eval=var_exists(c("SDEM004.bin", "WCWI005.SQ003."))}

# crosstab by gender 
df.geam %>% 
    print_xtable("WCWI005.SQ003.","SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCWI005.SQ003.", "SDEM004.bin")), fig.cap=get_caption("WCWI005.SQ003.", "SDEM004.bin", c(F,T) )}
df.geam %>% 
  print_xbarplot("SDEM004.bin", "WCWI005.SQ003.", legpos = "right", legdir = "vertical", ltitle=F, lwidth = 15)
```


\newpage




#### `r var_label("WCWI005.SQ004.")`


```{r eval=exechunk("WCWI005.SQ004."), fig.height=3, fig.cap=get_caption("WCWI005.SQ004.", topl=c(F,T))}

###############
# Job sharing with a colleague
###############

df.geam %>%
    print_barplot(WCWI005.SQ004.)

```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC001", "WCWI005.SQ004."))}

# crosstab by role 
df.geam %>% 
    print_xtable("WCWI005.SQ004.","WCJC001")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCWI005.SQ004.", "WCJC001")), fig.cap=get_caption("WCWI005.SQ004.", "WCJC001", c(F,T) )}
df.geam %>% 
  print_xbarplot("WCJC001", "WCWI005.SQ004.",xlangle=0, ltitle=F, legdir = "vertical", legpos = "right", lwidth = 10)
```


\newpage


```{r eval=var_exists(c("SDEM004.bin", "WCWI005.SQ004."))}

# crosstab by gender 
df.geam %>% 
    print_xtable("WCWI005.SQ004.","SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCWI005.SQ004.", "SDEM004.bin")), fig.cap=get_caption("WCWI005.SQ004.", "SDEM004.bin", c(F,T) )}
df.geam %>% 
  print_xbarplot("SDEM004.bin", "WCWI005.SQ004.", legpos = "right", legdir = "vertical", ltitle=F, lwidth = 10)
```


\newpage





### `r var_toplabel("EWCS89JobSatisfact8.SQ001.")`  `r if(lsVarCode) "(EWCS89JobSatisfact8)" `
<p>&nbsp;</p>


```{r eval=var_exists("EWCS89JobSatisfact8.SQ001."),fig.height=7, fig.width=8, fig.cap=get_caption("EWCS89JobSatisfact8.SQ001.")}

################################################
# Job satisfaction parent: EWCS89JobSatisfact8
################################################

df.geam %>% 
  select(starts_with("EWCS89JobSatisfact8.SQ")) %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors ="Set1", 
                show.n = F,
                show.total = F,
                geom.size = .5,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))

```


\newpage


```{r eval=exechunk("EWCS89JobSatisfact8.SQ001."), fig.height=3, fig.cap=get_caption("EWCS89JobSatisfact8.SQ001.", topl=c(F,T))}

###############
# Considering efforts, I feel I get paid appropriately
###############

df.geam %>%
    print_barplot(EWCS89JobSatisfact8.SQ001.)

```


<p>&nbsp;</p>


```{r eval=exechunk("EWCS89JobSatisfact8.SQ002."), fig.height=3, fig.cap=get_caption("EWCS89JobSatisfact8.SQ002.", topl=c(F,T))}

###############
# Job offers good prospoects for career advancement
###############

df.geam %>%
    print_barplot(EWCS89JobSatisfact8.SQ002.)
```


<p>&nbsp;</p>


```{r eval=exechunk("EWCS89JobSatisfact8.SQ003."), fig.height=3, fig.cap=get_caption("EWCS89JobSatisfact8.SQ003.", topl=c(F,T))}

###############
# Receive the recognition I deserve
###############

df.geam %>%
    print_barplot(EWCS89JobSatisfact8.SQ003.)
```


<p>&nbsp;</p>


```{r eval=exechunk("EWCS89JobSatisfact8.SQ004."), fig.height=3, fig.cap=get_caption("EWCS89JobSatisfact8.SQ004.", topl=c(F,T))}

###############
# Get on well with my colleagues
###############

df.geam %>%
    print_barplot(EWCS89JobSatisfact8.SQ004.)
```


<p>&nbsp;</p>


```{r eval=exechunk("EWCS89JobSatisfact8.SQ005."), fig.height=3, fig.cap=get_caption("EWCS89JobSatisfact8.SQ005.", topl=c(F,T))}

###############
# Motivated to give best performance
###############

df.geam %>%
    print_barplot(EWCS89JobSatisfact8.SQ005.)
```


<p>&nbsp;</p>


```{r eval=exechunk("EWCS89JobSatisfact8.SQ006."), fig.height=3, fig.cap=get_caption("EWCS89JobSatisfact8.SQ006.", topl=c(F,T))}

###############
# Personal life better due to job
###############

df.geam %>%
    print_barplot(EWCS89JobSatisfact8.SQ006.)
```


<p>&nbsp;</p>


```{r eval=exechunk("EWCS89JobSatisfact8.SQ007."), fig.height=3, fig.cap=get_caption("EWCS89JobSatisfact8.SQ007.", topl=c(F,T))}

###############
# Might loose job next 6 month
###############

df.geam %>%
    print_barplot(EWCS89JobSatisfact8.SQ007.)
```


<p>&nbsp;</p>


```{r eval=exechunk("EWCS89JobSatisfact8.SQ008."), fig.height=3, fig.cap=get_caption("EWCS89JobSatisfact8.SQ008.", topl=c(F,T))}

###############
# Easy to find a new job
###############

df.geam %>%
    print_barplot(EWCS89JobSatisfact8.SQ008.)
```
    
    
    
\newpage





### `r var_toplabel("EWCS36WorkIntensity2.SQ001.")`  `r if(lsVarCode) "(EWCS36WorkIntensity2)" `
<p>&nbsp;</p>


```{r eval=var_exists("EWCS36WorkIntensity2.SQ001."), fig.height=4.8, fig.cap=get_caption("EWCS36WorkIntensity2.SQ001.")}

################################################
# Work intensity parent: EWCS36WorkIntensity2
################################################


df.geam %>% 
  select(starts_with("EWCS36WorkIntensity2.SQ")) %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal,
                geom.size = .4,
                show.total = F, 
                digits = percdigits, 
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 12))

```


\newpage


#### `r var_label("EWCS36WorkIntensity2.SQ001.")`


```{r eval=exechunk("EWCS36WorkIntensity2.SQ001."), fig.height=3, fig.cap=get_caption("EWCS36WorkIntensity2.SQ001.", topl=c(F,T))}

###############
# ...at night, for at least 2 hours
###############

df.geam %>%
    print_barplot(EWCS36WorkIntensity2.SQ001.)

```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC001", "EWCS36WorkIntensity2.SQ001."))}

# crosstab by role 
df.geam %>% 
    print_xtable("EWCS36WorkIntensity2.SQ001.","WCJC001")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("EWCS36WorkIntensity2.SQ001.", "WCJC001")), fig.cap=get_caption("EWCS36WorkIntensity2.SQ001.", "WCJC001", c(F,T) )}
df.geam %>% 
  print_xbarplot("WCJC001","EWCS36WorkIntensity2.SQ001.", xlangle=0, ltitle=F, legdir = "vertical", legpos = "right", lwidth = 10)
```


\newpage


```{r eval=var_exists(c("SDEM004.bin", "EWCS36WorkIntensity2.SQ001."))}

# crosstab by gender 
df.geam %>% 
    print_xtable("EWCS36WorkIntensity2.SQ001.","SDEM004.bin")
```


<p>&nbsp;</p>
<p>&nbsp;</p>


```{r eval=var_exists(c("EWCS36WorkIntensity2.SQ001.", "SDEM004.bin")), fig.cap=get_caption("EWCS36WorkIntensity2.SQ001.", "SDEM004.bin", c(F,T) )}
df.geam %>% 
  print_xbarplot("SDEM004.bin","EWCS36WorkIntensity2.SQ001.", legpos = "right", legdir = "vertical", ltitle=F)
```


\newpage



#### `r var_label("EWCS36WorkIntensity2.SQ002.")`


```{r eval=exechunk("EWCS36WorkIntensity2.SQ002."), fig.height=3, fig.cap=get_caption("EWCS36WorkIntensity2.SQ002.", topl=c(F,T))}

###############
# ... on Sundays
###############

df.geam %>%
    print_barplot(EWCS36WorkIntensity2.SQ002.)
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC001", "EWCS36WorkIntensity2.SQ002."))}

# crosstab by role 
df.geam %>% 
    print_xtable("EWCS36WorkIntensity2.SQ002.","WCJC001")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("EWCS36WorkIntensity2.SQ002.", "WCJC001")), fig.cap=get_caption("EWCS36WorkIntensity2.SQ002.", "WCJC001", c(F,T) )}
df.geam %>% 
  print_xbarplot("WCJC001","EWCS36WorkIntensity2.SQ002.", xlangle=0, ltitle=F, legdir = "vertical", legpos = "right", lwidth=10)
```


\newpage


```{r eval=var_exists(c("SDEM004.bin", "EWCS36WorkIntensity2.SQ002."))}

# crosstab by gender 
df.geam %>% 
    print_xtable("EWCS36WorkIntensity2.SQ002.","SDEM004.bin")
```


<p>&nbsp;</p>
<p>&nbsp;</p>


```{r eval=var_exists(c("EWCS36WorkIntensity2.SQ002.", "SDEM004.bin")), fig.cap=get_caption("EWCS36WorkIntensity2.SQ002.", "SDEM004.bin", c(F,T) )}
df.geam %>% 
  print_xbarplot("SDEM004.bin","EWCS36WorkIntensity2.SQ002.", legpos = "right", legdir = "vertical", ltitle=F)
```

    
\newpage



#### `r var_label("EWCS36WorkIntensity2.SQ003.")`


```{r eval=exechunk("EWCS36WorkIntensity2.SQ003."), fig.height=3, fig.cap=get_caption("EWCS36WorkIntensity2.SQ003.", topl=c(F,T))}

###############
# ... on Saturdays
###############

df.geam %>%
    print_barplot(EWCS36WorkIntensity2.SQ003.)
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC001", "EWCS36WorkIntensity2.SQ003."))}

# crosstab by role 
df.geam %>% 
    print_xtable("EWCS36WorkIntensity2.SQ003.","WCJC001")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("EWCS36WorkIntensity2.SQ003.", "WCJC001")), fig.cap=get_caption("EWCS36WorkIntensity2.SQ003.", "WCJC001", c(F,T) )}
df.geam %>% 
  print_xbarplot("WCJC001","EWCS36WorkIntensity2.SQ003.", xlangle=0, ltitle=F, legdir = "vertical", legpos = "right", lwidth=10)
```


\newpage


```{r eval=var_exists(c("SDEM004.bin", "EWCS36WorkIntensity2.SQ003."))}

# crosstab by gender 
df.geam %>% 
    print_xtable("EWCS36WorkIntensity2.SQ003.","SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("EWCS36WorkIntensity2.SQ003.", "SDEM004.bin")), fig.cap=get_caption("EWCS36WorkIntensity2.SQ003.", "SDEM004.bin", c(F,T) )}
df.geam %>% 
  print_xbarplot("SDEM004.bin","EWCS36WorkIntensity2.SQ003.", legpos = "right", legdir = "vertical", ltitle=F)
```


\newpage




#### `r var_label("EWCS36WorkIntensity2.SQ004.")`


```{r eval=exechunk("EWCS36WorkIntensity2.SQ004."), fig.height=3, fig.cap=get_caption("EWCS36WorkIntensity2.SQ004.", topl=c(F,T))}

###############
# ... more than 10 hours a day
###############

df.geam %>%
    print_barplot(EWCS36WorkIntensity2.SQ004.)
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC001", "EWCS36WorkIntensity2.SQ004."))}

# crosstab by role 
df.geam %>% 
    print_xtable("EWCS36WorkIntensity2.SQ004.","WCJC001")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("EWCS36WorkIntensity2.SQ004.", "WCJC001")), fig.cap=get_caption("EWCS36WorkIntensity2.SQ004.", "WCJC001", c(F,T) )}
df.geam %>% 
  print_xbarplot("WCJC001","EWCS36WorkIntensity2.SQ004.", xlangle=0, ltitle=F, legdir = "vertical", legpos = "right", lwidth = 10)
```


\newpage


```{r eval=var_exists(c("SDEM004.bin", "EWCS36WorkIntensity2.SQ004."))}

# crosstab by gender 
df.geam %>% 
    print_xtable("EWCS36WorkIntensity2.SQ004.","SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("EWCS36WorkIntensity2.SQ004.", "SDEM004.bin")), fig.cap=get_caption("EWCS36WorkIntensity2.SQ004.", "SDEM004.bin", c(F,T) )}
df.geam %>% 
  print_xbarplot("SDEM004.bin","EWCS36WorkIntensity2.SQ004.", legpos = "right", legdir = "vertical", ltitle=F)
```


\newpage





### `r var_toplabel("WorkFamConfISSP.SQ001.")`  `r if(lsVarCode) "(WorkFamConfISSP)" `
<p>&nbsp;</p>


```{r eval=var_exists("WorkFamConfISSP.SQ001."), fig.height=5, fig.cap=get_caption("WorkFamConfISSP.SQ001.")}

################################################
# Work family conflict parent: WorkFamConfISSP
################################################

df.geam %>% 
  select(starts_with("WorkFamConfISSP.SQ")) %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal,
                geom.size = .4,
                show.total = F, 
                digits = percdigits, 
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 12))

```


\newpage



#### `r var_label("WorkFamConfISSP.SQ001.")`


```{r eval=exechunk("WorkFamConfISSP.SQ001."), fig.height=3, fig.cap=get_caption("WorkFamConfISSP.SQ001.", topl=c(F,T))}

###############
# come home from work too tired
###############

df.geam %>%
    print_barplot(WorkFamConfISSP.SQ001.)

```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC001", "WorkFamConfISSP.SQ001."))}

# crosstab by role 
df.geam %>% 
    print_xtable("WorkFamConfISSP.SQ001.","WCJC001")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WorkFamConfISSP.SQ001.", "WCJC001")), fig.cap=get_caption("WorkFamConfISSP.SQ001.", "WCJC001", c(F,T) )}
df.geam %>% 
  print_xbarplot("WCJC001","WorkFamConfISSP.SQ001.", xlangle=0, ltitle=F, legdir = "vertical", legpos = "right", lwidth=10)
```


\newpage


```{r eval=var_exists(c("SDEM004.bin", "WorkFamConfISSP.SQ001."))}

# crosstab by gender 
df.geam %>% 
    print_xtable("WorkFamConfISSP.SQ001.","SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WorkFamConfISSP.SQ001.", "SDEM004.bin")), fig.cap=get_caption("WorkFamConfISSP.SQ001.", "SDEM004.bin", c(F,T) )}
df.geam %>% 
  print_xbarplot("SDEM004.bin","WorkFamConfISSP.SQ001.", legpos = "right", legdir = "vertical", ltitle=F, lwidth=10)
```


\newpage




#### `r var_label("WorkFamConfISSP.SQ002.")`


```{r eval=exechunk("WorkFamConfISSP.SQ002."), fig.height=3, fig.cap=get_caption("WorkFamConfISSP.SQ002.", topl=c(F,T))}

###############
# difficult to fulfill commitments personal life due to work
###############

df.geam %>%
    print_barplot(WorkFamConfISSP.SQ002.)
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC001", "WorkFamConfISSP.SQ002."))}

# crosstab by role 
df.geam %>% 
    print_xtable("WorkFamConfISSP.SQ002.","WCJC001")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WorkFamConfISSP.SQ002.", "WCJC001")), fig.cap=get_caption("WorkFamConfISSP.SQ002.", "WCJC001", c(F,T) )}
df.geam %>% 
  print_xbarplot("WCJC001", "WorkFamConfISSP.SQ002.", xlangle=0, ltitle=F, legdir = "vertical", legpos = "right", lwidth=10)
```


\newpage


```{r eval=var_exists(c("SDEM004.bin", "WorkFamConfISSP.SQ002."))}

# crosstab by gender 
df.geam %>% 
    print_xtable("WorkFamConfISSP.SQ002.","SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WorkFamConfISSP.SQ002.", "SDEM004.bin")), fig.cap=get_caption("WorkFamConfISSP.SQ002.", "SDEM004.bin", c(F,T) )}
df.geam %>% 
  print_xbarplot("SDEM004.bin","WorkFamConfISSP.SQ002.", legpos = "right", legdir = "vertical", ltitle=F, lwidth=10)
```

    
\newpage



#### `r var_label("WorkFamConfISSP.SQ003.")`


```{r eval=exechunk("WorkFamConfISSP.SQ003."), fig.height=3, fig.cap=get_caption("WorkFamConfISSP.SQ003.", topl=c(F,T))}

###############
# too tired at work due to household 
###############

df.geam %>%
    print_barplot(WorkFamConfISSP.SQ003.)
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC001", "WorkFamConfISSP.SQ003."))}

# crosstab by role 
df.geam %>% 
    print_xtable("WorkFamConfISSP.SQ003.","WCJC001")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WorkFamConfISSP.SQ003.", "WCJC001")), fig.cap=get_caption("WorkFamConfISSP.SQ003.", "WCJC001", c(F,T) )}
df.geam %>% 
  print_xbarplot("WCJC001","WorkFamConfISSP.SQ003.", xlangle=0, ltitle=F, legdir = "vertical", legpos = "right", lwidth=10)
```


\newpage


```{r eval=var_exists(c("SDEM004.bin", "WorkFamConfISSP.SQ003."))}

# crosstab by gender 
df.geam %>% 
    print_xtable("WorkFamConfISSP.SQ003.","SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WorkFamConfISSP.SQ003.", "SDEM004.bin")), fig.cap=get_caption("WorkFamConfISSP.SQ003.", "SDEM004.bin", c(F,T) )}
df.geam %>% 
  print_xbarplot("SDEM004.bin", "WorkFamConfISSP.SQ003.", legpos = "right", legdir = "vertical", ltitle=F, lwidth=10)
```

    
\newpage




#### `r var_label("WorkFamConfISSP.SQ004.")`
<p>&nbsp;</p>


```{r eval=exechunk("WorkFamConfISSP.SQ004."), fig.height=3, fig.cap=get_caption("WorkFamConfISSP.SQ004.", topl=c(F,T))}

###############
# difficult to concentrate at work due to personal committments. 
###############

df.geam %>%
    print_barplot(WorkFamConfISSP.SQ004.)
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC001", "WorkFamConfISSP.SQ004."))}

# crosstab by role 
df.geam %>% 
    print_xtable("WorkFamConfISSP.SQ004.","WCJC001")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WorkFamConfISSP.SQ004.", "WCJC001")), fig.cap=get_caption("WorkFamConfISSP.SQ004.", "WCJC001", c(F,T) )}
df.geam %>% 
  print_xbarplot("WCJC001","WorkFamConfISSP.SQ004.", xlangle=0, ltitle=F, legdir = "vertical", legpos = "right", lwidth=10)
```


\newpage


```{r eval=var_exists(c("SDEM004.bin", "WorkFamConfISSP.SQ004."))}

# crosstab by gender 
df.geam %>% 
    print_xtable("WorkFamConfISSP.SQ004.","SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WorkFamConfISSP.SQ004.", "SDEM004.bin")), fig.cap=get_caption("WorkFamConfISSP.SQ004.", "SDEM004.bin", c(F,T) )}
df.geam %>% 
  print_xbarplot("SDEM004.bin", "WorkFamConfISSP.SQ004.", legpos = "right", legdir = "vertical", ltitle=F, lwidth=10)
```


\newpage





### `r var_toplabel("Covid.SQ01.")`  `r if(lsVarCode) "(Covid)" `
<p>&nbsp;</p>


```{r eval=exechunk("Covid.SQ01."), fig.height=8.5, fig.width=7, fig.cap=get_caption("Covid.SQ01.")}

################################################
# Covid 
################################################
df.geam %>% 
  select(starts_with("Covid.SQ")) %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors ="Set1", 
                show.n = F, 
                show.total=F,
                digits = percdigits,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 12))


```



    
\newpage



```{r eval=exechunk("Covid.SQ01."), fig.height=3, fig.cap=get_caption("Covid.SQ01.", topl=c(F,T))}

###############
# I've had more time to write academic papers
###############

df.geam %>%
    print_barplot(Covid.SQ01.)

```


<p>&nbsp;</p>


```{r eval=exechunk("Covid.SQ02."), fig.height=3, fig.cap=get_caption("Covid.SQ02.", topl=c(F,T))}

###############
# Not been able to concentrate on work 
###############

df.geam %>%
    print_barplot(Covid.SQ02.)
```


<p>&nbsp;</p>


```{r eval=exechunk("Covid.SQ03."), fig.height=3, fig.cap=get_caption("Covid.SQ03.", topl=c(F,T))}

###############
# I have received enough support from my family or friends
###############

df.geam %>%
    print_barplot(Covid.SQ03.)
```


<p>&nbsp;</p>


```{r eval=exechunk("Covid.SQ04."), fig.height=3, fig.cap=get_caption("Covid.SQ04.", topl=c(F,T))}

###############
# Due to restrictions in relation to the COVID-19 pandemic, it has been impossible for me to conduct my research (e.g. closure
# of laboratory, no access to study participants)
###############

df.geam %>%
    print_barplot(Covid.SQ04.)
```


<p>&nbsp;</p>


```{r eval=exechunk("Covid.SQ05."), fig.height=3, fig.cap=get_caption("Covid.SQ05.", topl=c(F,T))}

###############
# My household conditions have made it hard for me to work (e.g. lack of office space, constant presence of other people)
###############

df.geam %>%
    print_barplot(Covid.SQ05.)
```


<p>&nbsp;</p>


```{r eval=exechunk("Covid.SQ06."), fig.height=3, fig.cap=get_caption("Covid.SQ06.", topl=c(F,T))}

###############
# I have been overwhelmed by the switch to the online teaching
###############

df.geam %>%
    print_barplot(Covid.SQ06.)
```


<p>&nbsp;</p>


```{r eval=exechunk("Covid.SQ07."), fig.height=3, fig.cap=get_caption("Covid.SQ07.", topl=c(F,T))}

###############
# Due to my caring responsibilities resulting from pandemic restrictions, I have had less time for my research
###############

df.geam %>%
    print_barplot(Covid.SQ07.)
```


<p>&nbsp;</p>


```{r eval=exechunk("Covid.SQ08."), fig.height=3, fig.cap=get_caption("Covid.SQ08.", topl=c(F,T))}

###############
# My psychological wellbeing has deteriorated
###############

df.geam %>%
    print_barplot(Covid.SQ08.)
```


<p>&nbsp;</p>


```{r eval=exechunk("Covid.SQ09."), fig.height=3, fig.cap=get_caption("Covid.SQ09.", topl=c(F,T))}

###############
# Promotion postponed
###############

df.geam %>%
    print_barplot(Covid.SQ09.)
```


<p>&nbsp;</p>


```{r eval=exechunk("Covid.SQ10."), fig.height=3, fig.cap=get_caption("Covid.SQ10.", topl=c(F,T))}

###############
# Enough support from my institution
###############

df.geam %>%
    print_barplot(Covid.SQ10.)
```

    
\newpage



















