## Work-life Balance

Includes questions 14-21, codes: WCWI006, WCWI008, WCWI009, WCWI010, WCWI005, EWCS89JobSatisfact8, EWCS36WorkIntensity2, WorkFamConfISSP 


### `r if (!is.null(data$WCWI006)) get_label(data$WCWI006)`

```{r primecare, eval=!is.null(data$WCWI006) }

data %>% 
    filter(!is.na(WCWI006) & hideNA) %>% 
    ggplot(aes(x=WCWI006)) + 
    geom_bar()+ 
    labs(title="") +
    theme_light() +
    theme(axis.title.x = element_blank())
```

```{r primecare_tab, eval=!is.null(data$WCWI006)}
print_frqtable(data$WCWI006) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$WCWI008)) get_label(data$WCWI008)`
```{r guardian18, eval=!is.null(data$WCWI008) }

# parent or legal guardian for children 18 years or younger

data %>% 
    filter(!is.na(WCWI008) & hideNA) %>% 
    ggplot(aes(x=WCWI008)) + 
    geom_bar()+ 
    labs(title="") +
    theme_light() +
    theme(axis.title.x = element_blank())
```

```{r guardian18_tab, eval=!is.null(data$WCWI008)}
print_frqtable(data$WCWI008) 
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$WCWI005_SQ001)) attr(data$WCWI005_SQ001, "question_label")`

```{r eval=!is.null(data$WCWI005_SQ001), fig.height=4, fig.width=10}

data %>%
  select(starts_with("WCWI005_SQ0")) %>%
  plot_likert(geom.colors=pal6, values="show", show.prc.sign=T, catcount = 4, cat.neutral = NULL) + 
  #theme_sjplot(base_size = 20, base_family = "")
  #font_size(title=10, axis_title.x=10, axis_title.y=12, labels.x=8, labels.y=12)
  theme_light() +
  theme(axis.text.y = element_text(size=11))

```
<p>&nbsp;</p>
<p>&nbsp;</p>



### `r if (!is.null(data$EWCS89JobSatisfact8_SQ001)) attr(data$EWCS89JobSatisfact8_SQ001, "question_label")`

```{r eval=!is.null(data$EWCS89JobSatisfact8_SQ001), fig.height=8, fig.width=10}
data %>%
  select(starts_with("EWCS89JobSatisfact8_SQ0")) %>%
  plot_likert(geom.colors=pal6, values="show", show.prc.sign=T, catcount = 4, cat.neutral = 3) + 
  theme_light()

```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$EWCS36WorkIntensity2_SQ001)) attr(data$EWCS36WorkIntensity2_SQ001, "question_label")`

```{r eval=!is.null(data$EWCS36WorkIntensity2_SQ001), fig.height=3, fig.width=10}
data %>%
  select(starts_with("EWCS36WorkIntensity2_SQ0")) %>%
  plot_likert(geom.colors=pal6, values="show", show.prc.sign=T, catcount = 4, cat.neutral = NULL) + 
  theme_light()
```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$WorkFamConfISSP_SQ001)) attr(data$WorkFamConfISSP_SQ001, "question_label")`

```{r eval=!is.null(data$WorkFamConfISSP_SQ001), fig.height=4, fig.width=10}
data %>%
  select(starts_with("WorkFamConfISSP_SQ0")) %>%
  plot_likert(geom.colors=pal6, values="show", show.prc.sign=T, catcount = 4, cat.neutral = NULL) + 
  theme_light()

```
<p>&nbsp;</p>
<p>&nbsp;</p>

























