## Parental Leave


### `r var_toplabel("WCWI011a")`  `r if(lsVarCode) "(WCWI011a)" `
<p>&nbsp;</p>


```{r eval=exechunk("WCWI011a"), fig.cap=get_caption("WCWI011a")}

################################################
# Have you ever taken, or are you currently taking any form or parental leave? 
################################################

df.geam %>%
    print_barplot(WCWI011a)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI011a")}
df.geam %>% 
    print_frqtable("WCWI011a") 
```


\newpage


```{r eval=var_exists(c("SDEM004.bin", "WCWI011a"))}

# crosstab by gender 
df.geam %>% 
    print_xtable("WCWI011a","SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("WCWI011a", "SDEM004.bin")), fig.cap=get_caption("WCWI011a", "SDEM004.bin", c(F,T) )}
df.geam %>% 
  print_xbarplot("SDEM004.bin","WCWI011a", legpos = "right", legdir = "vertical", ltitle=F, lwidth=10)
```


\newpage




### `r var_toplabel("WCWI011b.SQ001.")`  `r if(lsVarCode) "(WCWI011b)" `
<p>&nbsp;</p>
<p>&nbsp;</p>


```{r eval=exechunk("WCWI011b.SQ001."), fig.height=3, fig.cap=get_caption("WCWI011b.SQ001.")}

################################################
# Which of the following forms of leave have you taken / or are you currently taking?
################################################

df.geam %>%
    select(starts_with("WCWI011b.SQ")) %>%
    plot_likert(geom.colors=cpal, 
              values="sum.outside", 
              show.n = T, 
              show.prc.sign=T, 
              sort.frq = "pos.asc", 
              geom.size = .4,
              reverse.scale = T,
              show.legend = F,
              digits = percdigits,
              grid.range = c(1,.2),
              wrap.labels = 50) + 
    theme_light() + 
    theme(legend.position = "bottom", 
          axis.text.x=element_blank(),
          axis.text = element_text(size = 12))
``` 


\newpage




### `r var_toplabel("WCWI014")`  `r if(lsVarCode) "(WCWI014)" `
<p>&nbsp;</p>


```{r eval=exechunk("WCWI014"), fig.cap=get_caption("WCWI014") }

################################################
# Overall, how much time have you spent on any form of parental leave? 
################################################

df.geam %>%
    print_barplot(WCWI014, xlangle = 60)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI014")}
df.geam %>% 
    print_frqtable("WCWI014") 
```
    
\newpage




### `r var_toplabel("WCWI015")`  `r if(lsVarCode) "(WCWI015)" `
<p>&nbsp;</p>


```{r eval=exechunk("WCWI015"), fig.cap=get_caption("WCWI015") }

################################################
# How long ago did you return to work from your most recent period of parental leave? 
################################################

df.geam %>%
    print_barplot(WCWI015)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI015")}
df.geam %>% 
    print_frqtable("WCWI015") 
```
    
\newpage





### `r var_toplabel("WCWI016.SQ001.")`  `r if(lsVarCode) "(WCWI016)" `
<p>&nbsp;</p>


```{r eval=var_exists("WCWI016.SQ001."), fig.height=7, fig.width=8, fig.cap=get_caption("WCWI016.SQ001.")}

################################################
# Availability of options either before, during or upon your return from your most recent/current parental leave at your 
# organization.
################################################

df.geam %>% 
  select(starts_with("WCWI016.SQ")) %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .4,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))

```


\newpage


```{r eval=exechunk("WCWI016.SQ001."), fig.height=3, fig.cap=get_caption("WCWI016.SQ001.", topl=c(F,T))}

###############
# Keeping in touch with the institution while away
###############

df.geam %>%
    print_barplot(WCWI016.SQ001.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI016.SQ002."), fig.height=3, fig.cap=get_caption("WCWI016.SQ002.", topl=c(F,T))}

###############
# "Agreement on flexible working-time arrangements 
###############

df.geam %>%
    print_barplot(WCWI016.SQ002.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI016.SQ003."), fig.height=3, fig.cap=get_caption("WCWI016.SQ003.", topl=c(F,T))}

###############
# Agreement on flexible workplace arrangements 
###############

df.geam %>%
    print_barplot(WCWI016.SQ003.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI016.SQ004."), fig.height=3, fig.cap=get_caption("WCWI016.SQ004.", topl=c(F,T))}

###############
# Agreement on temporary reduction of workload
###############

df.geam %>%
    print_barplot(WCWI016.SQ004.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI016.SQ005."), fig.height=3, fig.cap=get_caption("WCWI016.SQ005.", topl=c(F,T))}

###############
# Childcare services at workplace
###############

df.geam %>%
    print_barplot(WCWI016.SQ005.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI016.SQ006."), fig.height=3, fig.cap=get_caption("WCWI016.SQ006.", topl=c(F,T))}

###############
# Childcare related policies at workplace, including payments and benefits
###############

df.geam %>%
    print_barplot(WCWI016.SQ006.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI016.SQ007."), fig.height=3, fig.cap=get_caption("WCWI016.SQ007.", topl=c(F,T))}

###############
# Compensations or extensions for existing deadlines
###############

df.geam %>%
    print_barplot(WCWI016.SQ007.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI016.SQ008."), fig.height=3, fig.cap=get_caption("WCWI016.SQ008.", topl=c(F,T))}

###############
# Adapted criteria for evaluation in annual performance review
###############

df.geam %>%
    print_barplot(WCWI016.SQ008.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI016.SQ009."), fig.height=3, fig.cap=get_caption("WCWI016.SQ009.", topl=c(F,T))}

###############
# Health and safety assessment
###############

df.geam %>%
    print_barplot(WCWI016.SQ009.)
```
    
\newpage





### `r var_toplabel("WCWI018.SQ001.")`  `r if(lsVarCode) "(WCWI018)" `
<p>&nbsp;</p>


```{r eval=var_exists("WCWI018.SQ001."), fig.height=7, fig.width=8, fig.cap=get_caption("WCWI018.SQ001.")}

################################################
# Please indicate how helpful each of the following was in preparing you for your parental leave:
################################################

df.geam %>% 
  select(starts_with("WCWI018.SQ")) %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .4,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))


```


\newpage


```{r eval=exechunk("WCWI018.SQ001."), fig.height=3, fig.cap=get_caption("WCWI018.SQ001.", topl=c(F,T))}

###############
# Information on childcare related policies, including payments and benefits
###############

df.geam %>%
    print_barplot(WCWI018.SQ001.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI018.SQ002."), fig.height=3, fig.cap=get_caption("WCWI018.SQ002.", topl=c(F,T))}

###############
# Facilities for continued baby feeding on return to work
###############

df.geam %>%
    print_barplot(WCWI018.SQ002.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI018.SQ003."), fig.height=3, fig.cap=get_caption("WCWI018.SQ003.", topl=c(F,T))}

###############
# Contacts for support services
###############

df.geam %>%
    print_barplot(WCWI018.SQ003.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI018.SQ004."), fig.height=3, fig.cap=get_caption("WCWI018.SQ004.", topl=c(F,T))}

###############
# Health and safety assessment
###############

df.geam %>%
    print_barplot(WCWI018.SQ004.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI018.SQ005."), fig.height=3, fig.cap=get_caption("WCWI018.SQ005.", topl=c(F,T))}

###############
# Time off for hospital or doctor's appointments
###############

df.geam %>%
    print_barplot(WCWI018.SQ005.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI018.SQ006."), fig.height=3, fig.cap=get_caption("WCWI018.SQ006.", topl=c(F,T))}

###############
# Information on how and when to notify the organization of your intentions regarding your return to work post-leave
###############

df.geam %>%
    print_barplot(WCWI018.SQ006.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI018.SQ007."), fig.height=3, fig.cap=get_caption("WCWI018.SQ007.", topl=c(F,T))}

###############
# Workplace childcare facilities
###############

df.geam %>%
    print_barplot(WCWI018.SQ007.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI018.SQ008."), fig.height=3, fig.cap=get_caption("WCWI018.SQ008.", topl=c(F,T))}

###############
# Information regarding leave cover
###############

df.geam %>%
    print_barplot(WCWI018.SQ008.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI018.SQ009."), fig.height=3, fig.cap=get_caption("WCWI018.SQ009.", topl=c(F,T))}

###############
# Sufficient time for handing responsibilities over to other staff
###############

df.geam %>%
    print_barplot(WCWI018.SQ009.)
```
    
    
\newpage






### `r var_toplabel("WCWI020")`  `r if(lsVarCode) "(WCWI020)" `
<p>&nbsp;</p>


```{r eval=exechunk("WCWI020"), fig.cap=get_caption("WCWI020") }

################################################
# Most recent parental leave: preparedness.  
################################################

df.geam %>%
    print_barplot(WCWI020, xlangle = 60)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI020")}
df.geam %>% 
    print_frqtable("WCWI020") 
```
    
    
\newpage






### `r var_toplabel("WCWI021.SQ001.")`  `r if(lsVarCode) "(WCWI021)" `
<p>&nbsp;</p>


```{r eval=var_exists("WCWI021.SQ001."), fig.height=8, fig.width=8, fig.cap=get_caption("WCWI021.SQ001.")}

################################################
# Please indicate how helpful each of the following was in facilitating your return after parental leave 
################################################

df.geam %>% 
  select(starts_with("WCWI021.SQ")) %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .4,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))

```


\newpage


```{r eval=exechunk("WCWI021.SQ001."), fig.height=3, fig.cap=get_caption("WCWI021.SQ001.", topl=c(F,T))}

###############
# Keeping in touch with the institution while away 
###############

df.geam %>%
    print_barplot(WCWI021.SQ001.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI021.SQ002."), fig.height=3, fig.cap=get_caption("WCWI021.SQ002.", topl=c(F,T))}

###############
# Agreement on flexible working-time arrangements 
###############

df.geam %>%
    print_barplot(WCWI021.SQ002.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI021.SQ003."), fig.height=3, fig.cap=get_caption("WCWI021.SQ003.", topl=c(F,T))}

###############
# Agreement on flexible workplace arrangements
###############

df.geam %>%
    print_barplot(WCWI021.SQ003.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI021.SQ004."), fig.height=3, fig.cap=get_caption("WCWI021.SQ004.", topl=c(F,T))}

###############
# Agreement on temporary reduction of workload related to specific tasks
###############

df.geam %>%
    print_barplot(WCWI021.SQ004.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI021.SQ005."), fig.height=3, fig.cap=get_caption("WCWI021.SQ005.", topl=c(F,T))}

###############
# Childcare services at workplace
###############

df.geam %>%
    print_barplot(WCWI021.SQ005.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI021.SQ006."), fig.height=3, fig.cap=get_caption("WCWI021.SQ006.", topl=c(F,T))}

###############
# Childcare related policies at workplace, including payments and benefits
###############

df.geam %>%
    print_barplot(WCWI021.SQ006.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI021.SQ007."), fig.height=3, fig.cap=get_caption("WCWI021.SQ007.", topl=c(F,T))}

###############
# Compensations or extensions for existing deadlines
###############

df.geam %>%
    print_barplot(WCWI021.SQ007.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI021.SQ008."), fig.height=3, fig.cap=get_caption("WCWI021.SQ008.", topl=c(F,T))}

###############
# Adapted criteria for evaluation in annual performance review
###############

df.geam %>%
    print_barplot(WCWI021.SQ008.)
```


<p>&nbsp;</p>


```{r eval=exechunk("WCWI021.SQ009."), fig.height=3, fig.cap=get_caption("WCWI021.SQ009.", topl=c(F,T))}

###############
# Health and safety assessment
###############

df.geam %>%
    print_barplot(WCWI021.SQ009.)
```
    
    
\newpage
