# Organizational Culture & Climate


## Perceptions of Recruitment

Includes questions 38-41, codes: BACD003, BACD005, BACD007, GlickMasculCont8

### `r if (!is.null(data$BACD003_SQ001)) attr(data$BACD003_SQ001, "question_label")`

```{r eval=!is.null(data$BACD003_SQ001), fig.height=6, fig.width=10}
data %>%
  select(starts_with("BACD003_SQ")) %>%
  plot_likert(geom.colors=pal6, values="show", show.prc.sign=T, catcount = 4, cat.neutral = NULL) + 
  theme_light()

```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$BACD005_SQ001)) attr(data$BACD005_SQ001, "question_label")`

```{r eval=!is.null(data$BACD005_SQ001), fig.height=6, fig.width=10}
data %>%
  select(starts_with("BACD005_SQ")) %>%
  plot_likert(geom.colors=pal6, values="show", show.prc.sign=T, catcount = 4, cat.neutral = NULL) + 
  theme_light()

```
<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$BACD007)) get_label(data$BACD007)`

```{r eval=!is.null(data$BACD007), fig.height=4, fig.width=10}
data %>% 
    filter(!is.na(BACD007) & hideNA) %>% 
    ggplot(aes(x=BACD007, fill=BACD007)) + 
    geom_bar() + 
    coord_flip() + 
    labs(y="Total count") +
    guides(fill=F) +
    theme_light() +
    theme(axis.title.y=element_blank())
```

```{r eval=!is.null(data$BACD007)}
print_frqtable(data$BACD007)
```


<p>&nbsp;</p>
<p>&nbsp;</p>


### `r if (!is.null(data$GlickMasculCont8_SQ001)) attr(data$GlickMasculCont8_SQ001, "question_label")`

```{r eval=!is.null(data$GlickMasculCont8_SQ001), fig.height=6, fig.width=10}
data %>%
  select(starts_with("GlickMasculCont8_SQ")) %>%
  plot_likert(geom.colors=pal6, values="show", show.prc.sign=T, catcount = 4, cat.neutral =3) + 
  theme_light()

```
<p>&nbsp;</p>
<p>&nbsp;</p>





