# Organizational Culture & Climate


## Perceptions of Recruitment


### `r var_toplabel("BACD003.SQ001.")`  `r if(lsVarCode) "(BACD003)" `
<p>&nbsp;</p>


```{r eval=var_exists("BACD003.SQ001."), fig.height=6, fig.width=8, fig.cap=get_caption("BACD003.SQ001.")}

################################################
# Please indicate how important each of the following were when deciding to apply for or take up 
# the post in your current institution:
################################################


df.geam %>% 
  select(starts_with("BACD003.SQ")) %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .4,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))

```


\newpage


```{r eval=exechunk("BACD003.SQ001."), fig.height=3}

###############
# Flexible working hours
###############

df.geam %>%
    print_barplot(BACD003.SQ001.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BACD003.SQ002."), fig.height=3}

###############
# Worklife balance 
###############

df.geam %>%
    print_barplot(BACD003.SQ002.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BACD003.SQ003."), fig.height=3}

###############
# Childcare facilities
###############

df.geam %>%
    print_barplot(BACD003.SQ003.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BACD003.SQ004."), fig.height=3}

###############
# Diverse inclusive work environment
###############

df.geam %>%
    print_barplot(BACD003.SQ004.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BACD003.SQ005."), fig.height=3}

###############
# Equality or diversity staff networks within the organization"
###############

df.geam %>%
    print_barplot(BACD003.SQ005.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BACD003.SQ006."), fig.height=3}

###############
# The reputation for training or career development offered by the organization or department
###############

df.geam %>%
    print_barplot(BACD003.SQ006.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BACD003.SQ007."), fig.height=3}

###############
# Not needing to relocate geographically
###############

df.geam %>%
    print_barplot(BACD003.SQ007.)
```
    
\newpage






### `r var_toplabel("BACD005.SQ001.")`  `r if(lsVarCode) "(BACD005)" `
<p>&nbsp;</p>


```{r eval=var_exists("BACD005.SQ001."), fig.height=9, fig.width=8, fig.cap=get_caption("BACD005.SQ001.")}

################################################
# If you were considering to apply for a promotion, how important would the following items be to you?"
################################################

df.geam %>% 
  select(starts_with("BACD005.SQ")) %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .4,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))

```


\newpage


```{r eval=exechunk("BACD005.SQ001."), fig.height=3}

###############
# Meeting the essential criteria outlined in the job description
###############

df.geam %>%
    print_barplot(BACD005.SQ001.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BACD005.SQ002."), fig.height=3}

###############
# Being encouraged to apply by your manager or a senior member of staff
###############

df.geam %>%
    print_barplot(BACD005.SQ002.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BACD005.SQ003."), fig.height=3}

###############
# Having a mentor to discuss and review your application
###############

df.geam %>%
    print_barplot(BACD005.SQ003.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BACD005.SQ004."), fig.height=3}

###############
# Whether the role accommodates flexible working arrangements
###############

df.geam %>%
    print_barplot(BACD005.SQ004.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BACD005.SQ005."), fig.height=3}

###############
# Opportunity for a pay or salary increase"
###############

df.geam %>%
    print_barplot(BACD005.SQ005.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BACD005.SQ006."), fig.height=3}

###############
# Opportunity to develop new skills/take on new responsibilities
###############

df.geam %>%
    print_barplot(BACD005.SQ006.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BACD005.SQ007."), fig.height=3}

###############
# Obtaining a more senior job title"
###############

df.geam %>%
    print_barplot(BACD005.SQ007.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BACD005.SQ008."), fig.height=3}

###############
#Having access to information regarding the application and promotion process
###############

df.geam %>%
    print_barplot(BACD005.SQ008.)
```
    
    
\newpage
   





### `r var_toplabel("BACD007")`  `r if(lsVarCode) "(BACD007)" `
<p>&nbsp;</p>


```{r eval=var_exists("BACD007"), fig.cap=get_caption("BACD007") }

################################################
# Hypothetically, when applying for a promotion or new post, what proportion of the 
# essential criteria do you need to meet to submit an application?
################################################

df.geam %>%
    print_barplot(BACD007, xlangle = 60, lwidth = 30)
```


<p>&nbsp;</p>


```{r eval=var_exists("BACD007")}
df.geam %>% 
    print_frqtable("BACD007") 
```
    
    
\newpage






### `r var_toplabel("GlickMasculCont8.SQ001.")`  `r if(lsVarCode) "(GlickMasculCont8)" `
<p>&nbsp;</p>


```{r eval=var_exists("GlickMasculCont8.SQ001."), fig.height=7, fig.width=8, fig.cap=get_caption("GlickMasculCont8.SQ001.")}

################################################
# In my work environment - Glick Masculinity Contest Culture 
################################################

df.geam %>% 
  select(starts_with("GlickMasculCont8.SQ")) %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .5,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 12))

```


\newpage


```{r eval=exechunk("GlickMasculCont8.SQ001."), fig.height=3}

###############
# Admitting you don't know the answer looks weak
###############

df.geam %>%
    print_barplot(GlickMasculCont8.SQ001.)
```


<p>&nbsp;</p>


```{r eval=exechunk("GlickMasculCont8.SQ002."), fig.height=3}

###############
# Expressing any emotion other than anger or pride is seen as weak
###############

df.geam %>%
    print_barplot(GlickMasculCont8.SQ002.)
```


<p>&nbsp;</p>


```{r eval=exechunk("GlickMasculCont8.SQ006."), fig.height=3}

###############
# It's important to be in good physical shape to be respected
###############

df.geam %>%
    print_barplot(GlickMasculCont8.SQ006.)
```


<p>&nbsp;</p>


```{r eval=exechunk("GlickMasculCont8.SQ007."), fig.height=3}

###############
# People who are physically smaller have to work harder to get respect
###############

df.geam %>%
    print_barplot(GlickMasculCont8.SQ007.)
```


<p>&nbsp;</p>


```{r eval=exechunk("GlickMasculCont8.SQ011."), fig.height=3}

###############
# To succeed you can't let family interfere with work
###############

df.geam %>%
    print_barplot(GlickMasculCont8.SQ011.)
```


<p>&nbsp;</p>


```{r eval=exechunk("GlickMasculCont8.SQ012."), fig.height=3}

###############
# Taking days off is frowned upon
###############

df.geam %>%
    print_barplot(GlickMasculCont8.SQ012.)
```


<p>&nbsp;</p>


```{r eval=exechunk("GlickMasculCont8.SQ016."), fig.height=3}

###############
# You're either \"in\" or you're \"out\", and once you're out, you're out"
###############

df.geam %>%
    print_barplot(GlickMasculCont8.SQ016.)
```


<p>&nbsp;</p>


```{r eval=exechunk("GlickMasculCont8.SQ017."), fig.height=3}

###############
# If you don't stand up for yourself people will step on you"
###############

df.geam %>%
    print_barplot(GlickMasculCont8.SQ017.)
```
    
    
\newpage
  



