## Perceptions of Gender Equality 


### `r var_toplabel("OCPER001.SQ001.")`  `r if(lsVarCode) "(OCPER001)" `
<p>&nbsp;</p>


```{r fig.height=7, fig.width=7, fig.cap=get_caption("OCPER001.SQ001.")}

################################################
# Please indicate the extent to which you agree or disagree with the following statements:
# regarding perception of gender equality 
################################################

df.geam %>% 
  select(starts_with("OCPER001.SQ")) %>% 
  #shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .5,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))

```


\newpage


```{r eval=exechunk("OCPER001.SQ001."), fig.height=3}

###############
# n general, men and women are equally represented
###############

df.geam %>%
    print_barplot(OCPER001.SQ001.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER001.SQ002."), fig.height=3}

###############
# In general, men and women are treated equally in my institution
###############

df.geam %>%
    print_barplot(OCPER001.SQ002.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER001.SQ003."), fig.height=3}

###############
#My institution is committed to promoting gender equality"
###############

df.geam %>%
    print_barplot(OCPER001.SQ003.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER001.SQ004."), fig.height=3}

###############
# Myself and colleagues know who to go to if we have concerns related to gender equality"
###############

df.geam %>%
    print_barplot(OCPER001.SQ004.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER001.SQ005."), fig.height=3}

###############
# My institution is responsive to concerns about gender equality"
###############

df.geam %>%
    print_barplot(OCPER001.SQ005.)
```
    
    
\newpage





### `r var_toplabel("OCPER002.SQ001.")`  `r if(lsVarCode) "(OCPER002)" `
<p>&nbsp;</p>


```{r fig.width=7, fig.cap=get_caption("OCPER002.SQ001.")}

################################################
# How would you view the representation of men and women in your institution?
################################################

df.geam %>% 
  select(starts_with("OCPER002.SQ")) %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .5,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))

```


\newpage


```{r eval=exechunk("OCPER002.SQ001."), fig.height=3}

###############
# In general
###############

df.geam %>%
    print_barplot(OCPER002.SQ001.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER002.SQ002."), fig.height=3}

###############
# With regards to academic/ research staff?"
###############

df.geam %>%
    print_barplot(OCPER002.SQ002.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER002.SQ003."), fig.height=3}

###############
# Technnicians
###############

df.geam %>%
    print_barplot(OCPER002.SQ003.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER002.SQ004."), fig.height=3}

###############
# With regards to admin staff
###############

df.geam %>%
    print_barplot(OCPER002.SQ004.)
```
    
    
\newpage





### `r var_toplabel("OCPER003.SQ001.")`  `r if(lsVarCode) "(OCPER003)" `
<p>&nbsp;</p>

Part 1 of 3. 


```{r, fig.width=7, fig.height=7, fig.cap=get_caption("OCPER003.SQ001.")}

################################################
# Have you perceived a difference in the allocation of the following in your institution? 
################################################

df.geam %>% 
  select("OCPER003.SQ001.", "OCPER003.SQ002.", "OCPER003.SQ003.", "OCPER003.SQ004.",
         "OCPER003.SQ005.", "OCPER003.SQ006.", "OCPER003.SQ007.", "OCPER003.SQ008.", "OCPER003.SQ009.") %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .5,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))


```
    
    
\newpage 
    

### `r var_toplabel("OCPER003.SQ001.")`  `r if(lsVarCode) "(OCPER003)" `
<p>&nbsp;</p>

Part 2 of 3. 


```{r, fig.width=7, fig.height=7, fig.cap=get_caption("OCPER003.SQ001.")}

################################################
# Have you perceived a difference in the allocation of the following in your institution? 
################################################

df.geam %>% 
  select("OCPER003.SQ010.", "OCPER003.SQ011.", "OCPER003.SQ012.", "OCPER003.SQ013.",
         "OCPER003.SQ014.", "OCPER003.SQ015.", "OCPER003.SQ016.", "OCPER003.SQ017.", "OCPER003.SQ018.") %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .5,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))


```

    
\newpage 

    

### `r var_toplabel("OCPER003.SQ001.")`  `r if(lsVarCode) "(OCPER003)" `
<p>&nbsp;</p>

Part 3 of 3. 


```{r, fig.width=7, fig.height=7, fig.cap=get_caption("OCPER003.SQ001.")}

################################################
# Have you perceived a difference in the allocation of the following in your institution? 
################################################

df.geam %>% 
  select("OCPER003.SQ019.", "OCPER003.SQ020.", "OCPER003.SQ021.", "OCPER003.SQ022.",
         "OCPER003.SQ023.", "OCPER003.SQ024.", "OCPER003.SQ025.", "OCPER003.SQ026.", "OCPER003.SQ027.") %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .5,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))


```


\newpage


```{r eval=exechunk("OCPER003.SQ001."), fig.height=3}

###############
# Attractive or desirable tasks or roles
###############

df.geam %>%
    print_barplot(OCPER003.SQ001.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ002."), fig.height=3}

###############
# Office space
###############

df.geam %>%
    print_barplot(OCPER003.SQ002.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ003."), fig.height=3}

###############
# The receipt of mentoring and/or other guidance in making career decisions
###############

df.geam %>%
    print_barplot(OCPER003.SQ003.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ004."), fig.height=3}

###############
# Representation senior positions
###############

df.geam %>%
    print_barplot(OCPER003.SQ004.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ005."), fig.height=3}

###############
# Responsibilities related to student care 
###############

df.geam %>%
    print_barplot(OCPER003.SQ005.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ006."), fig.height=3}

###############
# Positive attention from, or additional time with, senior management"
###############

df.geam %>%
    print_barplot(OCPER003.SQ006.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ007."), fig.height=3}

###############
# Access to informal circles of influence
###############

df.geam %>%
    print_barplot(OCPER003.SQ007.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ008."), fig.height=3}

###############
# Receiving positive feedback from management
###############

df.geam %>%
    print_barplot(OCPER003.SQ008.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ009."), fig.height=3}

###############
# Recruitment and selection of new staff"
###############

df.geam %>%
    print_barplot(OCPER003.SQ009.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ010."), fig.height=3}

###############
# Promotion decisions
###############

df.geam %>%
    print_barplot(OCPER003.SQ010.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ011."), fig.height=3}

###############
# Formal training and career development opportunities
###############

df.geam %>%
    print_barplot(OCPER003.SQ011.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ012."), fig.height=3}

###############
# Teching responsibilities 
###############

df.geam %>%
    print_barplot(OCPER003.SQ012.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ013."), fig.height=3}

###############
# Laboratory space, facilities or equipment"
###############

df.geam %>%
    print_barplot(OCPER003.SQ013.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ014."), fig.height=3}

###############
# Invitations or opportunities 
###############

df.geam %>%
    print_barplot(OCPER003.SQ014.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ015."), fig.height=3}

###############
# Appointments to editorships of journals, committees and panels"
###############

df.geam %>%
    print_barplot(OCPER003.SQ015.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ016."), fig.height=3}

###############
# Recognition of intellectual contributions during meetings, conferences, workshops, etc. 
###############

df.geam %>%
    print_barplot(OCPER003.SQ016.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ017."), fig.height=3}

###############
# Principal investigator roles
###############

df.geam %>%
    print_barplot(OCPER003.SQ017.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ018."), fig.height=3}

###############
# Funds and monetary resources
###############

df.geam %>%
    print_barplot(OCPER003.SQ018.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ019."), fig.height=3}

###############
# Awards and recognition of excellence
###############

df.geam %>%
    print_barplot(OCPER003.SQ019.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ020."), fig.height=3}

###############
# PhD and Masters students
###############

df.geam %>%
    print_barplot(OCPER003.SQ020.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ021."), fig.height=3}

###############
# Supervision responsibilities (for undergraduate and graduate students)
###############

df.geam %>%
    print_barplot(OCPER003.SQ021.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ022."), fig.height=3}

###############
# Specific counselling for qualifying candidates for recruitment 
###############

df.geam %>%
    print_barplot(OCPER003.SQ022.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ023."), fig.height=3}

###############
# "Support in grant preparation and writing"
###############

df.geam %>%
    print_barplot(OCPER003.SQ023.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ024."), fig.height=3}

###############
# The administration of harassment and hate crime reporting
###############

df.geam %>%
    print_barplot(OCPER003.SQ024.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ025."), fig.height=3}

###############
# "Student acknowledgement (e.g., recognizing feedback and guidance, teaching and mentoring)"
###############

df.geam %>%
    print_barplot(OCPER003.SQ025.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ026."), fig.height=3}

###############
# Dealing with staff or student grievances or queries"
###############

df.geam %>%
    print_barplot(OCPER003.SQ026.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER003.SQ027."), fig.height=3}

###############
# Authorship opportunities (including first author, corresponding author, senior author, etc.)"
###############

df.geam %>%
    print_barplot(OCPER003.SQ027.)
```
    
    
\newpage
  




### `r var_toplabel("OCPER004")`  `r if(lsVarCode) "(OCPER004)" `
<p>&nbsp;</p>


```{r val=exechunk("OCPER004"), fig.cap=get_caption("OCPER004")}

################################################
# When comparing the ease with which individuals can reach senior positions in your institution, it is in general:
################################################

df.geam %>%
    print_barplot(OCPER004, lwidth = 15, xlangle = 60)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCPER004")}
df.geam %>% 
    print_frqtable("OCPER004") 
```
    
    
\newpage






### `r var_toplabel("OCWC002.SQ001.")`  `r if(lsVarCode) "(OCWC002)" `
<p>&nbsp;</p>

Part 1 of 3 

```{r fig.width=7, fig.height=7, fig.cap=get_caption("OCWC002.SQ001.")}

################################################
# Please indicate the extent to which you agree or disagree with the following statements 
# relating to life in your current workplace:
################################################

df.geam %>% 
  select("OCWC002.SQ001.", "OCWC002.SQ002.", "OCWC002.SQ003.", "OCWC002.SQ004.", "OCWC002.SQ005.", 
         "OCWC002.SQ006.", "OCWC002.SQ007.", "OCWC002.SQ008.", "OCWC002.SQ009.") %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .5,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))

```
    
    
\newpage
    
    
### `r var_toplabel("OCWC002.SQ001.")`  `r if(lsVarCode) "(OCWC002)" `
<p>&nbsp;</p>

Part 2 of 3. 

```{r fig.width=7, fig.height=7,  fig.cap=get_caption("OCWC002.SQ001.")}

################################################
# Please indicate the extent to which you agree or disagree with the following statements 
# relating to life in your current workplace:
################################################

df.geam %>% 
  select("OCWC002.SQ010.", "OCWC002.SQ011.", "OCWC002.SQ012.", "OCWC002.SQ013.", "OCWC002.SQ014.", 
         "OCWC002.SQ015.", "OCWC002.SQ016.", "OCWC002.SQ017.", "OCWC002.SQ018.") %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .5,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))

```


\newpage
    
    
### `r var_toplabel("OCWC002.SQ001.")`  `r if(lsVarCode) "(OCWC002)" `
<p>&nbsp;</p>

Part 3 of 3. 


```{r fig.width=7, fig.height=5, fig.cap=get_caption("OCWC002.SQ001.")}

################################################
# Please indicate the extent to which you agree or disagree with the following statements 
# relating to life in your current workplace:
################################################

df.geam %>% 
  select("OCWC002.SQ019.", "OCWC002.SQ020.", "OCWC002.SQ021.", "OCWC002.SQ022.", "OCWC002.SQ023.") %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .5,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))

```


\newpage


```{r eval=exechunk("OCWC002.SQ001."), fig.height=3}

###############
# I work very hard, compared to others
###############

df.geam %>%
    print_barplot(OCWC002.SQ001.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ002."), fig.height=3}

###############
# My teaching is valued by students"
###############

df.geam %>%
    print_barplot(OCWC002.SQ002.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ003."), fig.height=3}

###############
# My teaching is valued by senior management"
###############

df.geam %>%
    print_barplot(OCWC002.SQ003.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ004."), fig.height=3}

###############
# Workload is allocated in a fair and transparent manner"
###############

df.geam %>%
    print_barplot(OCWC002.SQ004.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ005."), fig.height=3}

###############
# I often work long hours"
###############

df.geam %>%
    print_barplot(OCWC002.SQ005.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ006."), fig.height=3}

###############
# I could count on a good reference, if I needed one"
###############

df.geam %>%
    print_barplot(OCWC002.SQ006.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ007."), fig.height=3}

###############
#"The budget is allocated fairly"
###############

df.geam %>%
    print_barplot(OCWC002.SQ007.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ008."), fig.height=3}

###############
# "Laboratory and/or office space is allocated fairly"
###############

df.geam %>%
    print_barplot(OCWC002.SQ008.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ009."), fig.height=3}

###############
# If I needed to, I could relocate to another geographical location"
###############

df.geam %>%
    print_barplot(OCWC002.SQ009.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ010."), fig.height=3}

###############
# "I can count on the support of my family "
###############

df.geam %>%
    print_barplot(OCWC002.SQ010.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ011."), fig.height=3}

###############
# "I am involved in the social life of my institution"
###############

df.geam %>%
    print_barplot(OCWC002.SQ011.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ012."), fig.height=3}

###############
# Successes in my working life are celebrated by my colleagues"
###############

df.geam %>%
    print_barplot(OCWC002.SQ012.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ013."), fig.height=3}

###############
#I am encouraged to undertake activities that contribute to my career development"
###############

df.geam %>%
    print_barplot(OCWC002.SQ013.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ014."), fig.height=3}

###############
# I  have a formally assigned mentor who I see regularly"
###############

df.geam %>%
    print_barplot(OCWC002.SQ014.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ015."), fig.height=3}

###############
# I have the opportunity to serve on important institutional committees"
###############

df.geam %>%
    print_barplot(OCWC002.SQ015.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ016."), fig.height=3}

###############
# My research is valued by my colleagues"
###############

df.geam %>%
    print_barplot(OCWC002.SQ016.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ017."), fig.height=3}

###############
# I don’t have enough administrative experience
###############

df.geam %>%
    print_barplot(OCWC002.SQ017.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ018."), fig.height=3}

###############
# My institution values my external professional activities 
###############

df.geam %>%
    print_barplot(OCWC002.SQ018.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ019."), fig.height=3}

###############
# Senior staff are inaccessible to me
###############

df.geam %>%
    print_barplot(OCWC002.SQ019.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ020."), fig.height=3}

###############
# I have an unsupportive manager"
###############

df.geam %>%
    print_barplot(OCWC002.SQ020.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ021."), fig.height=3}

###############
# My work environment is friendly"
###############

df.geam %>%
    print_barplot(OCWC002.SQ021.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ022."), fig.height=3}

###############
#"Communication within my institution is poor"
###############

df.geam %>%
    print_barplot(OCWC002.SQ022.)
```


<p>&nbsp;</p>


```{r eval=exechunk("OCWC002.SQ023."), fig.height=3}

###############
# "My annual performance review is not useful or valuable for my development or progression"
###############

df.geam %>%
    print_barplot(OCWC002.SQ023.)
```
    
    
\newpage




### `r var_toplabel("r353q0")`  `r if(lsVarCode) "(r353q0)" `
<p>&nbsp;</p>


```{r val=exechunk("r353q0"), fig.cap=get_caption("r353q0") }

################################################
# In your opinion, have you observed progress in your organisation when it comes 
# to gender equality issues in the last 3 years?"
################################################

df.geam %>%
    print_barplot(r353q0, lwidth = 20, xlangle=60)
```


<p>&nbsp;</p>


```{r eval=exechunk("r353q0")}
df.geam %>% 
    print_frqtable("r353q0") 
```


\newpage


```{r eval=var_exists(c("WCJC001", "r353q0"))}

# crosstab by role 
df.geam %>% 
    print_xtable("r353q0","WCJC001")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("r353q0", "WCJC001")), fig.cap=get_caption("r353q0", "WCJC001", c(F,T) )}
df.geam %>% 
  print_xbarplot("WCJC001","r353q0", xlangle=0, ltitle=F, legdir = "vertical", legpos = "right", lwidth=10)
```


\newpage


```{r eval=var_exists(c("SDEM004.bin", "r353q0"))}

# crosstab by gender 
df.geam %>% 
    print_xtable("r353q0","SDEM004.bin")
```


<p>&nbsp;</p>


```{r eval=var_exists(c("r353q0", "SDEM004.bin")), fig.cap=get_caption("r353q0", "SDEM004.bin", c(F,T) )}
df.geam %>% 
  print_xbarplot("SDEM004.bin", "r353q0", legpos = "right", legdir = "vertical", ltitle=F, lwidth=10)
```


    
\newpage





### `r var_toplabel("r59q0.SQ001.")`  `r if(lsVarCode) "(r59q0)" `
<p>&nbsp;</p>
<p>&nbsp;</p>
```{r fig.cap=get_caption("r59q0.SQ001.")}

################################################
# In your opinion which of the following barriers affect the implementation of gender equality in your organisation? 
################################################

df.geam %>% 
  select(starts_with(("r59q0.SQ"))) %>% 
   shorten_label(maxlength = 50) %>% 
   plot_likert(geom.colors=cpal, 
              values="sum.outside", 
              show.n = F, 
              show.prc.sign=T, 
              sort.frq = "pos.asc", 
              geom.size = .4,
              reverse.scale = T,
              show.legend = F,
              digits = percdigits,
              grid.range = c(1,.2),
              wrap.labels = 60) + 
  theme_light() + 
  theme(legend.position = "bottom", 
         axis.text.x=element_blank(),
        axis.text = element_text(size = 11))


```


\newpage

    






