# Behavior

## Microagressions


### `r var_toplabel("BIMA001.SQ001.")`  `r if(lsVarCode) "(BIMA001)" `
<p>&nbsp;</p>


```{r fig.width=7, fig.height=8, fig.cap=get_caption("BIMA001.SQ001.")}

################################################
# The following items relate to your experience of microaggressions. Please rate how often you have experienced the 
# following  microaggressions within your workplace
################################################

df.geam %>% 
  select(starts_with("BIMA001.SQ")) %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .5,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))

```


\newpage


```{r eval=exechunk("BIMA001.SQ001."), fig.height=3}

###############
# I am often mistaken for being a lower-status worker
###############

df.geam %>%
    print_barplot(BIMA001.SQ001.)
```

```{r eval=exechunk("BIMA001.SQ002."), fig.height=3}

###############
# I am treated like a second-class citizen"
###############

df.geam %>%
    print_barplot(BIMA001.SQ002.)
```

```{r eval=exechunk("BIMA001.SQ003."), fig.height=3}

###############
# Sometimes I feel as if colleagues look past me or do not see me as a real person
###############

df.geam %>%
    print_barplot(BIMA001.SQ003.)
```

```{r eval=exechunk("BIMA001.SQ004."), fig.height=3}

###############
# My contributions are dismissed or devalued"
###############

df.geam %>%
    print_barplot(BIMA001.SQ004.)
```

```{r eval=exechunk("BIMA001.SQ005."), fig.height=3}

###############
# Colleagues have prejudices about my intelligence and abilities"
###############

df.geam %>%
    print_barplot(BIMA001.SQ005.)
```

```{r eval=exechunk("BIMA001.SQ006."), fig.height=3}

###############
# Others assume that I will act aggressively or are scared of me"
###############

df.geam %>%
    print_barplot(BIMA001.SQ006.)
```

```{r eval=exechunk("BIMA001.SQ007."), fig.height=3}

###############
# Colleagues ask me where I am from, suggesting that I do not belong
###############

df.geam %>%
    print_barplot(BIMA001.SQ007.)
```

```{r eval=exechunk("BIMA001.SQ008."), fig.height=3}

###############
# I notice that there are few role models in my institution with a similar background to my own"
###############

df.geam %>%
    print_barplot(BIMA001.SQ008.)
```

```{r eval=exechunk("BIMA001.SQ009."), fig.height=3}

###############
# Others hint that I should work hard to prove that I am not like other people from my background"
###############

df.geam %>%
    print_barplot(BIMA001.SQ009.)
```

```{r eval=exechunk("BIMA001.SQ010."), fig.height=3}

###############
# "Others suggest that people from my background get unfair benefits"
###############

df.geam %>%
    print_barplot(BIMA001.SQ010.)
```

```{r eval=exechunk("BIMA001.SQ011."), fig.height=3}

###############
# Some colleagues deny that people from my background face extra obstacles"
###############

df.geam %>%
    print_barplot(BIMA001.SQ011.)
```
    
    
\newpage






## Bullying Harassment 


### `r var_toplabel("BISB001.SQ001.")`  `r if(lsVarCode) "(BISB001)" `
<p>&nbsp;</p>


```{r, fig.width=7, fig.height=4.8, fig.cap=get_caption("BISB001.SQ001.")}

################################################
# The following questions are related to bullying and harassment within your workplace. How confident are you
# or would you be to report incidences of bullying and harassment to:"
################################################

df.geam %>% 
  select(starts_with("BISB001.SQ")) %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .5,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))

```


\newpage


```{r eval=exechunk("BISB001.SQ001."), fig.height=3}

###############
# Your manager within your institution"
###############

df.geam %>%
    print_barplot(BISB001.SQ001.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BISB001.SQ002."), fig.height=3}

###############
# A representative from Human Resources "
###############

df.geam %>%
    print_barplot(BISB001.SQ002.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BISB001.SQ003."), fig.height=3}

###############
# A senior colleague who is not your manager"
###############

df.geam %>%
    print_barplot(BISB001.SQ003.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BISB001.SQ004."), fig.height=3}

###############
# "A representative from a trade union"
###############

df.geam %>%
    print_barplot(BISB001.SQ004.)
```


<p>&nbsp;</p>


```{r eval=exechunk("BISB001.SQ005."), fig.height=3}

###############
# "A representative from your equality diversity and/or inclusion committee/ organisation
###############

df.geam %>%
    print_barplot(BISB001.SQ005.)
```
    
    
\newpage





### `r var_toplabel("BISB003")` `r if(lsVarCode) "(BISB003)" `
<p>&nbsp;</p>


```{r eval=exechunk("BISB003"), fig.cap=get_caption("BISB003") }

################################################
# During the last 12 months, have you personally experienced harassment and/or bullying in your institution?"
################################################

df.geam %>% 
    print_barplot(BISB003)
```

```{r eval=exechunk("BISB003")}
df.geam %>% 
    print_frqtable("BISB003")
```


\newpage


<p>&nbsp;</p>


```{r eval=var_exists(c("WCJC001", "BISB003"))}

# crosstab by role 
df.geam %>% 
    print_xtable("BISB003","WCJC001")
```


<p>&nbsp;</p>
<p>&nbsp;</p>


```{r eval=var_exists(c("BISB003", "WCJC001")), fig.cap=get_caption("BISB003", "WCJC001", c(F,T) )}
df.geam %>% 
  print_xbarplot("WCJC001","BISB003", xlangle=0, ltitle=F, legdir = "vertical", legpos = "right", lwidth=10)
```


\newpage


```{r eval=var_exists(c("SDEM004.bin", "BISB003"))}

# crosstab by gender 
df.geam %>% 
    print_xtable("BISB003","SDEM004.bin")
```


<p>&nbsp;</p>
<p>&nbsp;</p>


```{r eval=var_exists(c("BISB003", "SDEM004.bin")), fig.cap=get_caption("BISB003", "SDEM004.bin", c(F,T) )}
df.geam %>% 
  print_xbarplot("SDEM004.bin", "BISB003", legpos = "right", legdir = "vertical", ltitle=F, lwidth=10)
```


\newpage






### `r var_toplabel("BISB004.SQ001.")`  `r if(lsVarCode) "(BISB004)" `
<p>&nbsp;</p>


```{r eval=exechunk("BISB004.SQ001."), fig.height=3, fig.width=7, fig.cap=get_caption("BISB004.SQ001.")}

################################################
# Experienced sexual harassment / bullying. If yes, by whom? 
################################################

df.geam %>%
  select(starts_with("BISB004.SQ")) %>%
   plot_likert(geom.colors=cpal, 
              values="sum.outside", 
              show.n = F, 
              show.prc.sign=T, 
              sort.frq = "pos.asc", 
              geom.size = .4,
              reverse.scale = T,
              show.legend = F,
              digits = percdigits,
              grid.range = c(1,.2),
              wrap.labels = 50) + 
  theme_light() + 
  theme(legend.position = "bottom", 
         axis.text.x=element_blank(),
        axis.text = element_text(size = 12))
```
    
    
\newpage    
 





### `r var_toplabel("Neosexism.SQ002.")`  `r if(lsVarCode) "(Neosexism)" `
<p>&nbsp;</p>


```{r, fig.width=7, fig.height=9, fig.cap=get_caption("Neosexism.SQ002.")}

################################################
# Neosexism
################################################

df.geam %>% 
  select(starts_with("Neosexism.SQ")) %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal, 
                show.n = F,
                show.total = F,
                geom.size = .5,
                coord.flip = T,
                digits = 0,
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 11))



```

    
\newpage
