# (PART) Part - Exploring Relations {-}


# Work-Family Conflict Scale

Source: Breyer, B., and M. Bluemke. 2016. “Work-Family Conflict Scale (ISSP).” ZIS - The Collection Items and Scales for the Social Sciences. https://doi.org/10.6102/zis243.

The scale has been used in [2002](http://dx.doi.org/10.4232/1.11564) and [2012](http://dx.doi.org/10.4232/1.12022) in the Family and Changing Gender Roles module of the International Social Survey Program (ISSP). 


There are national reference values available to deduce if your respondents are below or above the national average of work conflict scale (see also [here](https://zis.gesis.org/skala/Breyer-Bluemke-Work-Family-Conflict-Scale-(ISSP)#Table6)) 

The scale is composed of four items which are subdivided in two dimensions: first, the degree of which work interferences with family (WF) and second, the degree of which family interferes with work (FW). 


|Code|Item            |Facet|
|----|----------------|-----|
|SQ001|I have come home from work too tired to do the chores which need to be done.|WF - work interferes with family|
|SQ002|It has been difficult for me to fulfil my family responsibilities because of the amount of time I spent on my job.|WF - work interferes with family|
|SQ003|I have arrived at work too tired to function well because of the household work I had done.|FW - family interferes with work|
|SQ004|I have found it difficult to concentrate at work because of my family responsibilities.|FW - family interferes with work|

The scale has been recoded, where 1 indicates a lower work-family conflict and 4 a higher work-family conflict. In the following table, higher mean values indicate higher work-family conflicts: 


```{r prepare_wf}

summarize_wf <- function(df){
    
    tbl <- df %>% 
        summarize(  Total  = n(), 
            total_wf = sum(!is.na(wf)),
            mean_wf = round(mean(wf, na.rm = T),3),
            sd_wf   = round(sd(wf, na.rm=T),3),
            total_fw = sum(!is.na(fw)),
            mean_fw = round(mean(fw, na.rm=T),3), 
            sd_fw   = round(sd(fw, na.rm=T),3), 
            mean_all= round(mean(all, na.rm=T),3))
    tbl
}


df.issp <- df.geam %>% 
    mutate(CareResp = if_else( (WCWI006 == "Yes" | WCWI008 == "Yes"), "Yes","No")) %>% 
    rowwise() %>% 
    mutate(wf = mean(c(WorkFamConfISSP.RE.SQ001., WorkFamConfISSP.RE.SQ002.), na.rm=T), 
           fw = mean(c(WorkFamConfISSP.RE.SQ003., WorkFamConfISSP.RE.SQ004.), na.rm=T), 
           all = (wf+fw)/2 ) %>% 
    ungroup()


```



```{r}
tbl1 <- summarize_wf(df.issp)%>% 
    select('Total WF'=total_wf, 
           'Mean Work-Family'=mean_wf, 
           'Total FW'=total_fw, 
           'Mean Family-Work'=mean_fw, 
           'Mean WF/FW' = mean_all)

print_misctable(tbl1, tcap="Mean Work-Family/Family-Work conflict values")
```


\newpage


## Gender differences 

Examining the Work-Family Conflict Scale by gender, the mean values of the scale change slightly as we exclude any respondent who has not indicated their gender. 

```{r}

tbl2 <- df.issp %>% 
    filter(!is.na(SDEM004.bin)) %>% 
    group_by(SDEM004.bin) %>% 
    summarize_wf() %>% 
    select(Gender=SDEM004.bin, 
                'Total WF'=total_wf, 
                'Mean Work-Family'=mean_wf, 
                'Total FW'=total_fw, 
                'Mean Family-Work'=mean_fw, 
                'Mean WF/FW' = mean_all)

diff.wf <- tbl2[1,3] - tbl2[2,3]
diff.fw <- tbl2[1,6] - tbl2[2,6]
    
print_misctable(tbl2, tcap="Mean Work-Family/Family-Work conflict values by gender")
    
```


```{r}

df.aov <- df.issp %>% 
    filter(!is.na(SDEM004.bin)) %>% 
    select(wf, fw, all, Gender=SDEM004.bin)

wf.aov <- aov(wf ~ Gender, data=df.aov)
fw.aov <- aov(fw ~ Gender, data=df.aov)

```

<p>&nbsp;</p>


### Work-family conflict by gender

There are `r if (!isig(wf.aov)) "**no**"` statistically **significant** differences for mean work-family conflict values by **gender**. Difference between mean values is *diff~|mean.wf-mean.wf|~=`r abs(diff.wf)`*


```{r}

print_aovtable(wf.aov, tcap="Anova Work-Family by Gender")

```

<p>&nbsp;</p>

### Family-work conflict by gender

There are `r if (!isig(fw.aov)) "**no**"` statistically **significant** differences for mean family-work conflict values by **gender**. Difference between mean values is *diff~|mean.fw-mean.fw|~=`r abs(diff.fw)`*

```{r}
print_aovtable(fw.aov, tcap="Anova Family-Work by Gender")
```


\newpage 


## Care responsibilities

Work-family conflict measures for respondents with care responsibilities. This includes both: care responsibilities for dependent adults (WCWI006) and care responsibilities for children (WCWI008). Care responsibilities have been aggregated into a new variable `CareResp` in case respondents have answered `YES` for either of `WCWI006`  or `WCWI008`. 


```{r}

tbl4 <- df.issp %>% 
    filter(!is.na(CareResp)) %>% 
    group_by(CareResp) %>% 
    summarize_wf() %>% 
    select('Care Resp.'=CareResp, 
                'Total WF'=total_wf, 
                'Mean Work-Family'=mean_wf, 
                'Total FW'=total_fw, 
                'Mean Family-Work'=mean_fw, 
                'Mean WF/FW' = mean_all)
    
diff.wf <- tbl4[1,3] - tbl4[2,3]
diff.fw <- tbl4[1,6] - tbl4[2,6]

print_misctable(tbl4, tcap="Mean Work-Family/Family-Work conflict values by Care Responsibilities")
```

Overall, we expect higher interference of family life with work in case respondents have care responsibilities. 

```{r}

df.aov <- df.issp %>% 
    filter(!is.na(CareResp)) %>% 
    select(wf, fw, all, CareResp)

wf.aov <- aov(wf ~ CareResp, data=df.aov)
fw.aov <- aov(fw ~ CareResp, data=df.aov)

```

<p>&nbsp;</p>


### Work-family conflict by care responsibilities

There are `r if (!isig(wf.aov)) "**no**"` statistically **significant** differences for mean work-family conflict values by **care responsibilities**. Difference between mean values is *diff~|mean.wf-mean.wf|~=`r abs(diff.wf)`*

```{r}

print_aovtable(wf.aov, tcap="Anova Work-Family by Care Responsibilities")

```

<p>&nbsp;</p>

### Family-work conflict by care responsibilities

There are `r if (!isig(fw.aov)) "**no**"` statistically **significant** differences for mean family-work conflict values by **care responsibilities**. Difference between mean values is *diff~|mean.fw-mean.fw|~=`r abs(diff.fw)`*

```{r}

print_aovtable(fw.aov, tcap="Anova Family-Work by Care Responsibilities")

```

\newpage


## Job Position 

We would expect that there are significant differences of work on family life for academic positions but not necessarily for other. 

```{r}

tbl5 <- df.issp %>% 
    filter(!is.na(WCJC001)) %>% 
    group_by(WCJC001) %>% 
    summarize_wf() %>% 
    select('Job position'=WCJC001, 
                'Total WF'=total_wf, 
                'Mean Work-Family'=mean_wf, 
                'Total FW'=total_fw, 
                'Mean Family-Work'=mean_fw, 
                'Mean WF/FW' = mean_all)


print_misctable(tbl5, tcap="Mean Work-Family/Family-Work conflict values by Job Position")
```

We expect higher interference of work with family from academic positions than technician or administrative staff. 

```{r}

df.aov <- df.issp %>% 
    filter(!is.na(WCJC001)) %>% 
    select(wf, fw, all, "Position"=WCJC001)

wfXJob.aov <- aov(wf ~ Position, data=df.aov)
fwXJob.aov <- aov(fw ~ Position, data=df.aov)

```



### Work-family conflict by job position

There are `r if (!isig(wfXJob.aov)) "**no**"` statistically **significant** differences for mean work-family conflict values by **job position**. 

```{r}

print_aovtable(wfXJob.aov, tcap="Anova Work-Family by Job Position")

```

<p>&nbsp;</p>
<p>&nbsp;</p>

```{r}
tuk.aov <- TukeyHSD(wfXJob.aov)

print_aovtable(tuk.aov, tcap="Work-Family score differences by job position")
```

<p>&nbsp;</p>
<p>&nbsp;</p>


### Family-work conflict by job position

There are `r if (!isig(fwXJob.aov)) "**no**"` statistically **significant** differences for mean family-work conflict values by **job position**. 

```{r}

print_aovtable(fwXJob.aov, tcap="Anova Family-Work by Job Position")

```

<p>&nbsp;</p>
<p>&nbsp;</p>

```{r}
tuk.aov <- TukeyHSD(fwXJob.aov)

print_aovtable(tuk.aov, tcap="Family-Work score differences by job position")
```



```{r workconflicissp_refs, eval=F}
library(XML)

rawTab <- htmlParse("data-raw/workfamconfISSP-refs.html")
df.ref <- readHTMLTable(rawTab['//table'][[1]])

names(df.ref) <- c("Country", "Gender", "Total", "meanWF", "sdWF", "meanFW", "sdFW", "meanAll", "sdAll")

df.ref <- df.ref[-c(1,2),]

if (knitr::is_html_output()){
    knitr::kable(df.ref)    
}

```



\newpage



