# Working overtime

There are four items used from the 5th and 6th European Working Conditions Survey to capture working overtime. The corresponding publications are: 

Eurofund, Francis Green, and Tarek Mostafa. 2012. “Trends in Job Quality in Europe. A Report   Based upon the 5th European Working Conditions Survey.” Luxembourg: Publications Office of the European Union. https://doi.org/10.2806/35164.

Parent-Thirion, Agnès, Isabella Biletta, Jorge Cabrita, Oscar Vargas, Greet Vermeylen, Aleksandra Wilcynska, and Mathijn Wilkens. 2016. “6th European Working Conditions Survey.” Publications Office of the European Union. https://www.eurofound.europa.eu/publications/report/2016/working-conditions/sixth-european-working-conditions-survey-overview-report.

Overall, the four items are: 

```{r prepare_overtime}

# prepare 
df.wi <- df.geam %>% 
    mutate(CareResp = if_else( (WCWI006 == "Yes" | WCWI008 == "Yes"), "Yes","No"),
           WI2RE.SQ001. = (as.numeric(EWCS36WorkIntensity2.SQ001.)-1), 
           WI2RE.SQ002. = (as.numeric(EWCS36WorkIntensity2.SQ002.)-1), 
           WI2RE.SQ003. = (as.numeric(EWCS36WorkIntensity2.SQ003.)-1), 
           WI2RE.SQ004. = (as.numeric(EWCS36WorkIntensity2.SQ004.)-1)) %>% 
    rowwise() %>% 
    mutate(WI2RE.Sum = sum(WI2RE.SQ001.,WI2RE.SQ002.,WI2RE.SQ003.,WI2RE.SQ004., na.rm=T))

```



```{r fig.height=4, fig.cap=get_caption("EWCS36WorkIntensity2.SQ001.")}

################################################
# Work intensity parent: EWCS36WorkIntensity2
################################################


df.geam %>% 
  select(starts_with("EWCS36WorkIntensity2.SQ")) %>% 
  shorten_label(maxlength = 50) %>% 
  plot_stackfrq(geom.colors =cpal,
                geom.size = .4,
                show.total = F, 
                digits = percdigits, 
                show.axis.prc = T) +
  theme_light() + 
  theme(legend.position = "bottom", 
        legend.direction = "vertical",
        legend.justification = c(1,0),
        axis.text.x=element_blank(),
        axis.text = element_text(size = 12))

```

<p>&nbsp;</p>

We can construct an overall index for work intensity by aggregating the numerical values across all four items. Scores are recoded as "0=Never", "1=Rarely", "2=Sometimes", and "3=Very often". Thus, "0=Never" responses will not contribute to the work-intensity index. The higher the mean score, the more frequently respondents work overtime. 

<p>&nbsp;</p>


## Working overtime by gender and job position

From the outset it is not clear if there is a difference in terms of working overtime between gender and job position. 

```{r}

tbl6 <- df.wi %>% 
    filter(!is.na(SDEM004.bin) & !is.na(WCJC001)) %>% 
    group_by(SDEM004.bin, WCJC001) %>% 
    summarize(total  = n(), 
              mean_wi = round(mean(WI2RE.Sum, na.rm = T),3))

names(tbl6) <- c("Gender", "Job Position", "Total", "Mean Work Overtime")

print_misctable(tbl6, tcap="Mean overtime by gender and job position")
```

<p>&nbsp;</p>

```{r}

df.aov <- df.wi %>% 
    filter(!is.na(SDEM004.bin) & !is.na(WCJC001)) %>% 
    select(Overtime=WI2RE.Sum, Gender=SDEM004.bin, Position=WCJC001)

wi2Xgender.aov <- aov(Overtime ~ Gender * Position, data=df.aov)

```

There are `r if (!isig(wi2Xgender.aov)) "**no**"` statistically **significant** differences for working overtime by **gender** and **job position**.

```{r}
print_aovtable(wi2Xgender.aov, tcap="Anova: Overtime differences by gender and position")

```

<p>&nbsp;</p>

By applying the Tukey HSD test, we can see for which concrete pairs `r if (!isig(wi2Xgender.aov)) "**significant**"`  differences of mean working overtime exist: 


```{r}
tuk.aov <- TukeyHSD(wi2Xgender.aov)

print_aovtable(tuk.aov, tcap="Group wise overtime differences by gender and job position")
```


\newpage


## Working Overtime by gender and type of contract

Working overtime could be more prone in contractual positions that are more precarious, i.e. part-time. 

```{r}


df.wi$WCJC011.RE <- df.wi$WCJC011

# which rows have "Other" or "I do not want to answer" for Gender? 
dropL <- which( (as.numeric(df.wi$WCJC011) == 3))
df.wi[dropL, "WCJC011.RE"] <- NA 


tbl7 <- df.wi %>% 
    filter(!is.na(SDEM004.bin) & !is.na(WCJC011.RE)) %>% 
    group_by(SDEM004.bin, WCJC011.RE) %>% 
    summarize(total  = n(), 
                mean_wi = round(mean(WI2RE.Sum, na.rm = T),3))

names(tbl7) <- c("Gender", "Type of Contract", "Total", "Mean Work Overtime")

print_misctable(tbl7, tcap="Mean overtime differences by gender and type of contract")

```

<p>&nbsp;</p>


```{r}
df.aov <- df.wi %>% 
    filter(!is.na(SDEM004.bin) & !is.na(WCJC011.RE)) %>% 
    select(Overtime=WI2RE.Sum, Gender=SDEM004.bin, Contract=WCJC011.RE)

wi2XGenderContract.aov <- aov(Overtime ~ Gender * Contract, data=df.aov)
```


There are `r if (!isig(wi2XGenderContract.aov)) "**no**"` statistically **significant** differences for working overtime by **gender** and **type of contract**.


```{r}
print_aovtable(wi2XGenderContract.aov, tcap="Anova: overtime differences by gender and type of contract")
```

By applying the Tukey HSD test, we can see for which concrete pairs `r if (!isig(wi2XGenderContract.aov)) "**significant**"`  differences of mean working overtime exist: 

```{r}
tuk.aov <- TukeyHSD(wi2XGenderContract.aov)

print_aovtable(tuk.aov, tcap="Group wise overtime differences by gender and type of contract")
```


\newpage


## Working Overtime by Gender and Age Group 

Working overtime could be related to age groups, i.e. the more experienced and older staff is, the more responsibilities they can have. 

```{r}

tbl8 <- df.wi %>% 
    filter(!is.na(SDEM004.bin) & !is.na(age_4g)) %>% 
    group_by(SDEM004.bin, age_4g) %>% 
    summarize(total  = n(), 
              mean_wi = round(mean(WI2RE.Sum, na.rm = T),3))

names(tbl8) <- c("Gender", "Age group", "Total", "Mean Work Overtime")

print_misctable(tbl8, tcap="Mean overtime by gender and age group")
```

<p>&nbsp;</p>

```{r}
df.aov <- df.wi %>% 
    filter(!is.na(SDEM004.bin) & !is.na(age_4g)) %>% 
    select(Overtime=WI2RE.Sum, Gender=SDEM004.bin, Age=age_4g)

wi2XGenderAge.aov <- aov(Overtime ~ Gender * Age, data=df.aov)
```

There are `r if (!isig(wi2XGenderAge.aov)) "**no**"` statistically **significant** differences for working overtime by **gender** and **age groups**.

```{r}
print_aovtable(wi2XGenderAge.aov, tcap="Anova: overtime differences by gender and age")
```

By applying the Tukey HSD test, we can see for which concrete pairs `r if (!isig(wi2XGenderAge.aov)) "**significant**"`  differences of mean working overtime exist: 

```{r}
tuk.aov <- TukeyHSD(wi2XGenderAge.aov)

print_aovtable(tuk.aov, tcap="Group wise overtime differences by gender and age")
```


\newpage


## Working overtime by gender and care responsibilities 

Working overtime could be related to care responsibilities as these interfere with work and push work tasks to off-hours. 

```{r}

tbl9 <- df.wi %>% 
    filter(!is.na(SDEM004.bin) & !is.na(CareResp)) %>% 
    group_by(SDEM004.bin, CareResp) %>% 
    summarize(total  = n(), 
              mean_wi = round(mean(WI2RE.Sum, na.rm = T),3))

names(tbl9) <- c("Gender", "Care Resp.", "Total", "Mean Work Overtime")

print_misctable(tbl9, tcap="Mean overtime by gender and care responsibilities")
```

<p>&nbsp;</p>

```{r}
df.aov <- df.wi %>% 
    filter(!is.na(SDEM004.bin) & !is.na(CareResp)) %>% 
    select(Overtime=WI2RE.Sum, Gender=SDEM004.bin, CareResp)

wi2XGenderCare.aov <- aov(Overtime ~ Gender * CareResp, data=df.aov)
```

There are `r if (!isig(wi2XGenderCare.aov)) "**no**"` statistically **significant** differences for working overtime by **gender** and **care responsibilities**.

```{r}
print_aovtable(wi2XGenderCare.aov, tcap="Anova: overtime differences by gender and care responsibilities")
```

By applying the Tukey HSD test, we can see for which concrete pairs `r if (!isig(wi2XGenderCare.aov)) "**significant**"`  differences of mean working overtime exist: 

```{r}
tuk.aov <- TukeyHSD(wi2XGenderCare.aov)

print_aovtable(tuk.aov, tcap="Group wise overtime differences by gender and care responsibilities")
```


\newpage






