# Wage Gap 

The wage gap is assessed by the salary information provided by respondents. It should be taken as an aproximative measure since the way respondents have calculated their salary is not clear. Objetive figures provided by Human Resources should be consulted in a second round. 

<p>&nbsp;</p>

## Mean wages by position and gender 

We expect a wage gap by position as well as by gender. 

```{r prepare_wagediff}

# Prepare
df.aov <- df.geam %>% 
    filter(!is.na(SDEM004.bin) & !is.na(WCJC001) & WCJC005 <= 10000) %>% 
    select(Gender=SDEM004.bin, Position=WCJC001, Salary=WCJC005)

tbl1 <- df.aov %>% 
  filter(Salary <= 10000 & !is.na(Gender)) %>% 
  group_by(Gender, Position) %>% 
  summarize("Mean Salary" = round(mean(Salary, na.rm = T),0))

print_misctable(tbl1, tcap="Mean salary by gender and job position")

```


```{r}
diffwage.aov <- aov(Salary ~ Gender * Position, data=df.aov)
```


There are `r if (!isig(diffwage.aov)) "**no**"` statistically **significant** wage gaps by **gender** and **job position**. Women indicate a lower salary compared to men at the same time that technicians and administrative staff indicate a lower salary than academic staff. 

```{r}
print_aovtable(diffwage.aov, tcap="Anova: Wage differences by gender and job position")
```


By applying the Tukey HSD test, we can see for which concrete pairs `r if (!isig(diffwage.aov)) "**significant**"`  differences of mean working overtime exist. 

It seems there is a wage gap between different job positions - which makes sense. Someone in an administrative position or a technician will have a lower salary as someone in an academic position. By studing the individual differences in wages, it appears that the gender differences although they do globally exist, are rather due to positions than gender per se. When comparing gender within each of the job positions, there are no significant differences within the same job position. 


```{r}
tuk.aov <- TukeyHSD(diffwage.aov)

print_aovtable(tuk.aov, tcap="Group wise wage differences by gender and job position")

```


\newpage


